---
title: "load_data"
author: "TB"
date: "5/15/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library("tibble")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("magrittr")
```

In this notebook we compare the migration results of the CP tracking with the matlab tracking results. 

CellProfiler tracking was performed using a the '2017_06_morph_gradient' pipeline. It uses a segmentation based on the morphological gradient; no preprocessing is performed to refine the tracks, i.e. LAP is not used. 


# Load tracking data tracking data 
```{r}
# define grouping variables 
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')

# result folder
analysis_folder <- '../../../analysis/2017_07_compare_tracking/'

population <- suppressMessages(read_csv(file.path(analysis_folder, 'clean_tracks_cp.csv'))) %>%
  mutate(Metadata_id = tolower(Metadata_id)) %>%
  group_by_(.dots = strata) 

```

A common problem in cell profiler tracking data is the so called 'two-objects' problem, i.e. two objects in the same frame belong to one path. This results in a wrong calculation of the speed. 
In the tracking data, these tracks can be identified using the 'Track_One_Cell'. 
```{r}
population %>% 
  ungroup() %>%
  group_by(Metadata_matrix, Metadata_condition) %>%
  summarise(quotient_good_tracks = sum(Track_One_Cell) / n(), n_bad_tracks = sum(Track_One_Cell == 0) )

population %>% 
  ungroup() %>%
  filter(Track_Length > 20) %>%
  group_by(Metadata_matrix) %>%
  summarise(good_tracks = n(), n_bad_tracks = sum(Track_One_Cell == 0), quotient_good_tracks = sum(Track_One_Cell) / n() )
```

For the following analysis all bad frames are removed. 
```{r}
population_2 <- population %>%
  filter(Track_One_Cell == 1)
```


To assess the tracking quality, we use cytominer::assess. The most interesting parameter is the VOT (valid observation time)
```{r}
quality <- cytominer::assess(population_2, 20, strata) 

quality %>%
  ungroup() %>%
  group_by(Metadata_matrix) %>%
  summarise(mean_VOT = mean(VOT), 
            sd_VOT = sd(VOT),
            mean_track_length = mean(Exp_Mean_Track_Length))

```

What are the worst and best IDs? 
```{r}
quality %>% 
  ungroup() %>%
  group_by(Metadata_matrix, Metadata_id) %>%
  na.omit() %>%
  summarise(mean_VOT = mean(VOT), 
          mean_track_length = mean(Exp_Mean_Track_Length)) %>%
  arrange(mean_VOT)
  
```

```{r}
quality %>% 
  ungroup() %>%
  group_by(Metadata_matrix, Metadata_condition) %>%
  na.omit() %>%
  summarise(mean_VOT = mean(VOT), 
          mean_track_length = mean(Exp_Mean_Track_Length)) %>%
  arrange(mean_VOT) 

```



```{r}
ggplot(quality, aes(x = VOT, y = Exp_Mean_Track_Length, color = Metadata_condition, size)) +
  geom_point() + 
  scale_colour_hue(c=70, l=80)
```
To further optimize the tracking using CP we select one data set that is used for further processing. This data set should include 
* many cells 
* many tracking errors (measured using Track_One_cell)

```{r}
tracks <- population %>%  
  ungroup() %>%
  group_by_(.dots = strata) %>%
  summarise(good_tracks = n(), n_bad_tracks = sum(Track_One_Cell == 0), quotient_good_tracks = sum(Track_One_Cell) / n() )

track_quality <- left_join(quality, tracks, by=strata)

ggplot(data=track_quality) + 
  aes(y = quotient_good_tracks, x = VOT, color = Metadata_id, shape = Metadata_dose) + 
  geom_point()
```

Is gn0040 a good candidate? the data looks promising but the image has many artefacts... 
```{r}
quality %>%  
  filter(Metadata_matrix == "FN", Metadata_condition == "CP17", Metadata_dose == 5, Metadata_id == "gn0040") %>% 
  print
```
What about gn0051, sp17, dose =5?
```{r}
track_quality %>%
  filter(Metadata_condition == "SP17", Metadata_dose == 5, Metadata_id == "gn0051") %>% 
  print
```
bd0053 control?
```{r}
track_quality %>% 
  filter(Metadata_condition == "vehicle", Metadata_id == "gn0051") %>% 
  print
```

```{r}
track_quality %>% 
  filter(Metadata_condition == "control", Metadata_id == "bd0073") %>% 
  print
```