---
title: "load_data"
author: "TB"
date: "5/15/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library("tibble")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("purrr")
library("broom")
library("dplyr")
library("tsne")
library("ggfortify")
library("cluster")
library("magrittr")
library("knitr")
library("corrplot")
source("windrose.r")
#library("cytominer")
# load cytominer 

```

# Load data 
The output of the MATLAB tracking is stored in "track.csv", see create_metadata.Rmd
```{r}
csv_in <- 'tracks.csv'
data_dir <- '../../analysis/2017_04_28_matlab/'
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')

tracks <- read_csv(file.path(data_dir, csv_in)) %>%
  select(Metadata_id,Metadata_matrix, Metadata_condition, Metadata_dose, everything() ) %>%
  arrange(Metadata_id, Metadata_matrix, Metadata_condition, Metadata_dose) %>%
  group_by_(.dots = strata) 
```

Assess the tracking quality. 
```{r}
quality <- tracks %>% 
  cytominer::assess(min_path_length = 19)

ggplot(data = quality, aes(x = VOT, y = Exp_Tracks, color = Metadata_id, shape = Metadata_condition)) +
   geom_point()
```


Small trajectories are removed and the angle is rotated by 90 degrees the angle is 
calculated using atan2 with 0 degree on "three o clock"; now we rotate 0 degree to the 
top. 

```{r}
population <- tracks %>%
  filter(Track_Length > 19) %>%
  mutate(Track_Angle = Track_Angle + pi/2) %>% # rotate all angles by 90 degree or pi/2
  mutate(Track_Angle = ifelse(Track_Angle > pi, Track_Angle - 2*pi, Track_Angle) ) %>%
  mutate(Track_Angle = ifelse(Track_Angle < 0, Track_Angle + 2*pi, Track_Angle) ) %>% 
  na.omit() %>%
  ungroup(.)
```

# Normalize data
Data normalization is performed using cytominer::normalize. Normalization is performed using the "control" group; these 
migrations have been run without chemotaxis (no IL-8, i.e. no chemoattractant)
```{r}
feature_var = c("Track_Speed","Track_Speed_Y","Track_Speed_X","Track_xFMI","Track_yFMI","Track_Directionality","Track_Distance_Traveled","Track_CI",)

population <- cytominer::generalized_log(population, variables = feature_var)

normalized <-
  cytominer::normalize(
    population = population,
    variables = feature_var,
    strata =  "Metadata_id",
    sample = population %>% filter(Metadata_condition == "control"),
    operation = "robustize"
  ) %>%
  mutate(Track_Angle = Track_Angle / pi)

normalized %<>% dplyr::collect() 
```


```{r}
data <- normalized %>% 
  select(one_of(c(feature_var)))

corrplot(cor(data))
population %>% filter(Metadata_condition == "control") %>% summarise(n = n())

```


Visualize data using tsne and pca
```{r}
feature_tsne = c(feature_var, "Track_Angle") 
train_data <- normalized %>% ungroup() %>% select_(.dots = feature_tsne)
```

```{r}
library("Rtsne")

plot_tsne <- function(train_data, data, perplexity = 50, title_name = "tsne with perplexity = 50"){
  tsne <- Rtsne(train_data, perplexity = perplexity, verbose = TRUE, max_iter = 500, theta = 0.5, pca_scale = TRUE)
  df <- cbind(data,as.data.frame(tsne$Y))
  ## plotting the results without clustering
  ggplot(data = df, aes(x = V1, y = V2, color = factor(Track_Sector), shape = Metadata_condition)) +
  geom_point() +
  xlab("") + ylab("") +
  ggtitle("t-SNE") +
  guides(colour = guide_legend(override.aes = list(size = 6))) +
  theme_light(base_size = 20) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank()) + 
  labs(title = title_name)
    
}

plot_tsne(train_data, normalized, 5, title_name = "tnse with perplexity = 5")
plot_tsne(train_data, normalized, 10, title_name = "tnse with perplexity = 10")
plot_tsne(train_data, normalized, 25, title_name = "tnse with perplexity = 25")
plot_tsne(train_data, normalized, 50, title_name = "tnse with perplexity = 50")
plot_tsne(train_data, normalized, 100, title_name = "tnse with perplexity = 100")
```

