---
title: "load_data"
author: "TB"
date: "5/15/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library("tibble")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("purrr")
library("broom")
library("dplyr")
library("tsne")
library("ggfortify")
library("cluster")
library("magrittr")
library("knitr")
library("corrplot")
source("windrose.r")
#library("cytominer")
# load cytominer 

```

# Load data 
The output of the MATLAB tracking is stored in "track.csv", see create_metadata.Rmd
```{r}
csv_in <- 'tracks.csv'
data_dir <- '../../analysis/2017_04_28_matlab/'
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')

tracks <- read_csv(file.path(data_dir, csv_in)) %>%
  select(Metadata_id,Metadata_matrix, Metadata_condition, Metadata_dose, everything() ) %>%
  arrange(Metadata_id, Metadata_matrix, Metadata_condition, Metadata_dose) %>%
  group_by_(.dots = strata) 
```

Assess the tracking quality. 
```{r}
quality <- tracks %>% 
  cytominer::assess(min_path_length = 19)

ggplot(data = quality, aes(x = VOT, y = Exp_Tracks, color = Metadata_id, shape = Metadata_condition)) +
   geom_point()
```


Small trajectories are removed and the angle is rotated by 90 degrees the angle is 
calculated using atan2 with 0 degree on "three o clock"; now we rotate 0 degree to the 
top. 

```{r}
population <- tracks %>%
  filter(Track_Length > 19) %>%
  mutate(Track_Angle = Track_Angle + pi/2) %>% # rotate all angles by 90 degree or pi/2
  mutate(Track_Angle = ifelse(Track_Angle > pi, Track_Angle - 2*pi, Track_Angle) ) %>%
  mutate(Track_Angle = ifelse(Track_Angle < 0, Track_Angle + 2*pi, Track_Angle) ) 

```

List all available experiments.
```{r}
population %>%
  select_(strata) %>%
  slice(1) %>%
  print()
```

Distribution of the direction and speed of the migration similar to a wind rose plot. 
We select the migrations run in Fibronectin and each condition (CP17, SP17, control 
and vehicle) is plotted separately.
```{r}
# select HEM matrix
test_data <- population %>%
  filter(Metadata_matrix == "HEM") 

CP17 <- test_data %>% 
  filter(Metadata_condition == "CP17") 
  #filter(Metadata_dose == 50) 
  
SP17 <- test_data %>% 
  filter(Metadata_condition == "SP17") 
  #filter(Metadata_dose == 50) 
  
controls <- test_data %>% 
  filter(Metadata_condition == "control") 

vehicle <- test_data %>% 
  filter(Metadata_condition == "vehicle") 
```

Plots for all four sections.

```{r}
source("windrose.r")

spdmin <- 0
spdmax <- 16
spdres <- 1
dirres <- 90
spdscale <- 1.5638 # factor to convert speed from pixel / frame to mum / min

h1 <- plot.windrose(spd = spdscale * CP17$Track_Speed, dir = (180 * (CP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Migration distribution CP17, all doses")

h2 <- plot.windrose(spd = spdscale * SP17$Track_Speed, dir = (180 * (SP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Migration distribution SP17, all doses")

h3 <- plot.windrose(spd = spdscale * controls$Track_Speed, dir = (180 * (controls$Track_Angle) / pi),
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Migration distribution control)")

h4 <- plot.windrose(spd = spdscale * vehicle$Track_Speed, dir = (180 * (vehicle$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres,  title_name = "Migration distribution vehicle")
```

Plots for all four sections.
```{r}
dirres <- 30

h1 <- plot.windrose(spd = spdscale * CP17$Track_Speed, dir = (180 * (CP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Migration distribution CP17, all doses")

h2 <- plot.windrose(spd = spdscale * SP17$Track_Speed, dir = (180 * (SP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Migration distribution SP17, all doses")

h3 <- plot.windrose(spd = spdscale * controls$Track_Speed, dir = (180 * (controls$Track_Angle) / pi),
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Migration distribution control)")

h4 <- plot.windrose(spd = spdscale * vehicle$Track_Speed, dir = (180 * (vehicle$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres,  title_name = "Migration distribution vehicle")
```
