---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library("tibble")
library("dplyr")
library("tidyr")
library("stringr")
library("knitr")
```

# Create Metadata for MATLAB tracking
Notebook to prepare Metadata file for MATLAB tracking data 

The metadata file for the matlab data is not in the same format as the cell profiler tracking data. Differences: 
1. The metadata file used for CellProfiler has an Metadata_dose column
2. The values in the column 'Metdata_condition' in the metadata file used for CellProfiler are 'CP17', 'SP17', 'vehicle' or 'control'

This notebook is used to create one csv file with the tracking results of all time series tracked with MATLAB and the same Metadata as used by CellProfiler. 

```{r}
# read metadata file available for matlab (old version)
metadata_matlab <- read_csv('../../load_data_csv/metadata_matlab_complete.csv') 

# read metadata file available for CellProfiler (new version)
metadata_cp <- read_csv('../../load_data_csv/file_list.csv') %>%
  print()

filename_csv_out <- '../../analysis/2017_04_28_matlab/TrackeddetectedNeutros.csv'

```

The date column is merged from the new Metadata_file. Note that the experiment ID is 
changed to lower case to enable a join. To unique the data, the group_by followed 
by an slice(1) is used. The last slice only removes one obsolete entry.
```{r}
metadata_date_id <-  metadata_cp %>% 
  select(Metadata_date, Metadata_id) %>%  
  mutate(Metadata_id = tolower(Metadata_id)) %>%
  group_by(Metadata_date, Metadata_id) %>%
  slice(1) %>% 
  ungroup %>% 
  slice(1:17) 
  
metadata_matlab %<>% 
  left_join(.,metadata_date_id, by = "Metadata_id") %>% 
  mutate(Metadata_dose = Metadata_condition) %>%
  rename(Metadata_condition2 = Metadata_condition) %>%
  print
```

Write CP17 / SP17 values to Metadata_condition; "control" and "vehicle" values are added later. 
```{r}
metadata_condition <-  metadata_cp %>% 
  select(Metadata_date, Metadata_id, Metadata_matrix, Metadata_condition) %>%  
  mutate(Metadata_id = tolower(Metadata_id)) %>%
  filter(str_detect(Metadata_condition, 'CP17|SP17')) %>%
  group_by(Metadata_date, Metadata_id, Metadata_matrix,Metadata_condition) %>%
  slice(1) %>% 
  ungroup
  
metadata_matlab %<>% 
  left_join(.,metadata_condition, by = c("Metadata_date", "Metadata_id", "Metadata_matrix")) %>% 
  print
```

Now the control and vehicle values are written to the Metadata_condition column. 
```{r}
metadata_matlab$Metadata_condition[metadata_matlab$Metadata_dose == "cont"] = 'control'
metadata_matlab$Metadata_condition[metadata_matlab$Metadata_dose == "vehi"] = 'vehicle'
metadata_matlab$Metadata_condition[metadata_matlab$Metadata_dose == "water"] = 'water'

metadata_matlab$Metadata_dose[metadata_matlab$Metadata_dose == "cont"] = 'None'
metadata_matlab$Metadata_dose[metadata_matlab$Metadata_dose == "vehi"] = 'None'
metadata_matlab$Metadata_dose[metadata_matlab$Metadata_dose == "water"] = 'None'
```

Arrange columns 
```{r}
metadata_matlab %<>%
  select(Metadata_date, Metadata_id, Metadata_matrix, Metadata_condition,Metadata_dose, everything() ) %>%
  select(-Metadata_condition2) %>% 
  print()
```

The variable metadata_matlab stores the metadata information for all tracking data. Now, we want to combine the 
metadata with the tracking results stored "featureList.csv". The path for each featureList is stored in the 
column metadata_matlab$File_Path. 

To merge the metadata with the values in the featureList.csv, we first load all tracking results as one large 
list with 76 entries. 


```{r}
file_list <- lapply(metadata_matlab$File_Path, function(i){
  file.path(i,'featureList.csv')
  })

population <- lapply(file_list, function(i){suppressMessages(read_csv(i))})

```

The metadata for the population is rewritten as a list. Then, the Map function is used to 
merge the population and the metadata list. The *do.call()* function is used to merge the list of 
data frames into one big data frame.
```{r}
metadata_list <- split(metadata_matlab, seq(nrow(metadata_matlab)))  

population <- Map(function(x,y){c(x,y)},population,metadata_list) 

population <- do.call(rbind, lapply(population,data.frame))

write_csv(population,filename_csv_out)
```


```{r}
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')

population %>% group_by_(.dots = strata) %>%
  select(Metadata_condition,Metadata_dose,Metadata_id,Metadata_date,Metadata_matrix,File_Path) %>%
  filter(Metadata_matrix == 'HEM') %>%
  slice(1) %>%
  knitr::kable()
```