---
title: "load_data"
author: "TB"
date: "5/15/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library("tibble")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("purrr")
library("broom")
library("dplyr")
library("tsne")
library("ggfortify")
library("cluster")
library("magrittr")
library("knitr")
library("corrplot")
```

# Load data 
The file tracks.csv contains the output of the cytominer::track function
```{r}
csv_in <- 'tracks.csv'
csv_normalized <- 'normalized.csv'
data_dir <- '../../analysis/2017_04_28_matlab/'
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')

tracks <- read_csv(file.path(data_dir, csv_in))
```

Small trajectories are removed and the angle is rotated by 90 degrees the angle is 
calculated using atan2 with 0 degree on "three o clock"; now we rotate 0 degree to the 
top. 

```{r}
population <- tracks %>%
  filter(Track_Length > 19) %>%
  mutate(Track_Angle = Track_Angle + pi/2) %>% # rotate all angles by 90 degree or pi/2
  mutate(Track_Angle = ifelse(Track_Angle > pi, Track_Angle - 2*pi, Track_Angle) ) %>%
  mutate(Track_Angle = ifelse(Track_Angle < 0, Track_Angle + 2*pi, Track_Angle) ) %>% 
  na.omit() %>%
  ungroup(.)
```

# Normalize data
Data normalization is performed using cytominer::normalize. Normalization is performed using the "control" group; these 
migrations have been run without chemotaxis (no IL-8, i.e. no chemoattractant). 

The angle is normalized to [-1,1]
```{r}
feature_var = c("Track_Speed","Track_Speed_Y","Track_Speed_X","Track_xFMI","Track_yFMI","Track_Directionality","Track_Distance_Traveled","Track_CI")

population <- cytominer::generalized_log(population, variables = feature_var)

normalized <-
  cytominer::normalize(
    population = population,
    variables = feature_var,
    strata =  "Metadata_id",
    sample = population %>% filter(Metadata_condition == "control"),
    operation = "robustize"
  ) %>%
  mutate(Track_Angle = Track_Angle / pi)

normalized %<>% dplyr::collect() 

```

## Save normalized data.
```{r}
write_csv(normalized, file.path(data_dir, csv_normalized))
```


Compare xFMI for our data set
```{r}
normalized %<>% dplyr::collect() 

ggplot(data = population, aes(x = Metadata_id, y = Track_xFMI)) +
  geom_boxplot() +
  ggtitle("xFMI not normalized")

ggplot(data = population %>% filter(Metadata_condition == "control"), aes(x = Metadata_id, y = Track_xFMI)) +
  geom_boxplot() +
  ggtitle("xFMI for control group not normalized")

ggplot(data = population %>% filter(Metadata_condition == "CP17"), aes(x = Metadata_id, y = Track_xFMI)) +
  geom_boxplot() +
  ggtitle("xFMI not normalized")
  

```

# Normalized vs. not normalized data
We analyze the effect of the normalization by visalizing different properties of the 
migration experiments run using Fibronektin
```{r}
test_data <-  population %>% 
  filter(Metadata_matrix == "FN") %>%
  filter(Metadata_condition != "water")

test_data_normalized <- normalized %>% 
  filter(Metadata_matrix == "FN") %>%
  filter(Metadata_condition != "water")

ggplot(data = test_data, aes(x = Metadata_condition, y = Track_xFMI)) +
  geom_boxplot() +
  ggtitle("Migration in FN, track length >=20")

ggplot(data = test_data_normalized, aes(x = Metadata_condition, y = Track_xFMI)) +
  geom_boxplot() +
  ggtitle("Migration in FN, track length >=20, normalized")
```

# Directionality
```{r}
ggplot(data = test_data, aes(x = Track_Directionality,fill = Metadata_condition)) + 
  geom_histogram(binwidth = 0.05) +
  ggtitle("Migration in FN, track length >=20")

ggplot(data = test_data_normalized, aes(x = Track_Directionality,fill = Metadata_condition)) + 
  geom_histogram(binwidth = 0.05) +
  ggtitle("Migration in FN, track length >=20, normalized")

```



# x forward migration index 
```{r}
ggplot(data = test_data, aes(x = Track_xFMI,fill = Metadata_condition)) + 
  geom_histogram(binwidth = 0.1) +
  ggtitle("Migration in FN, track length >=20")

ggplot(data = test_data, aes(x = Track_xFMI,colour = Metadata_condition)) + 
  geom_freqpoly(binwidth = 0.1) +
  ggtitle("Migration in FN, track length >=20")

ggplot(data = test_data_normalized, aes(x = Track_xFMI,fill = Metadata_condition)) + 
  geom_histogram(binwidth = 0.5) +
  ggtitle("Migration in FN, track length >=20, normalized")

ggplot(data = test_data_normalized, aes(x = Track_xFMI,colour = Metadata_condition)) + 
  geom_freqpoly(binwidth = 0.5) +
  ggtitle("Migration in FN, track length >=20, normalized")

```

# x forward migration index 
```{r}
ggplot(data = test_data, aes(x = Track_yFMI,fill = Metadata_condition)) + 
  geom_histogram(binwidth = 0.1) +
  ggtitle("Migration in FN, track length >=20")

ggplot(data = test_data, aes(x = Track_yFMI,colour = Metadata_condition)) + 
  geom_freqpoly(binwidth = 0.1) +
  ggtitle("Migration in FN, track length >=20")

ggplot(data = test_data_normalized, aes(x = Track_yFMI,fill = Metadata_condition)) + 
  geom_histogram(binwidth = 0.5) +
  ggtitle("Migration in FN, track length >=20, normalized")

ggplot(data = test_data_normalized, aes(x = Track_yFMI,colour = Metadata_condition)) + 
  geom_freqpoly(binwidth = 0.5) +
  ggtitle("Migration in FN, track length >=20, normalized")

```

```{r}

ggplot(data = test_data %>% filter(Metadata_condition != 'vehicle'), aes(x = Track_xFMI, y = Track_CI)) +
  geom_point(aes(colour = Metadata_condition)) +
  ggtitle("Migration in FN, track length >=20")
  
ggplot(data = test_data_normalized %>% filter(Metadata_condition != 'vehicle'), aes(x = Track_xFMI, y = Track_CI)) +
  geom_point(aes(colour = Metadata_condition))  +
  ggtitle("Migration in FN, track length >=20, normalized")
```


```{r}
ggplot(data = test_data_normalized %>% filter(Metadata_condition == 'CP17'), aes(x = factor(Track_Sector), y = Track_xFMI)) +
  geom_boxplot() +
  ggtitle("Migration in FN, track length >=20, normalized")

ggplot(data = test_data_normalized %>% filter(Metadata_condition == 'control'), aes(x = factor(Track_Sector), y = Track_xFMI)) +
  geom_boxplot( ) +
  ggtitle("Migration in FN, track length >=20, normalized")
```

```{r}
ggplot(data = test_data_normalized %>% filter(Metadata_condition == 'CP17'), aes(x = factor(Track_Sector), y = Track_CI)) +
  geom_boxplot() +
  ggtitle("Migration in FN, track length >=20, normalized")

ggplot(data = test_data_normalized %>% filter(Metadata_condition == 'control'), aes(x = factor(Track_Sector), y = Track_CI)) +
  geom_boxplot( ) +
  ggtitle("Migration in FN, track length >=20, normalized")

ggplot(data = test_data_normalized %>% filter(Metadata_condition == 'SP17'), aes(x = factor(Track_Sector), y = Track_CI)) +
  geom_boxplot() +
  ggtitle("Migration in FN, track length >=20, normalized")

ggplot(data = test_data_normalized %>% filter(Metadata_condition == 'vehicle'), aes(x = factor(Track_Sector), y = Track_CI)) +
  geom_boxplot( ) +
  ggtitle("Migration in FN, track length >=20, normalized")
```


```{r}
ggplot(data = test_data_normalized %>% filter(Metadata_condition == 'control'), aes(x = Metadata_id, y = Track_xFMI)) +
  geom_boxplot( outlier.shape = NA) +
  ggtitle("Migration in FN, track length >=20, normalized")

ggplot(data = test_data_normalized %>% filter(Metadata_condition == 'CP17'), aes(x = Metadata_id, y = Track_xFMI)) +
  geom_boxplot( outlier.shape = NA) +
  ggtitle("Migration in FN, track length >=20, normalized")
```
# cluster the data 
```{r}
data <- normalized %>% 
  select(one_of(c(feature_var, 'Track_Angle')))

corrplot(cor(data))
```