---
title: "Normalize Cell Tracking Ddata"
author: "Tim Becker "
date: "5/15/2017"
output: html_document
---

```{r setup, include=FALSE}
library("readr")
library("tibble")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("purrr")
library("broom")
library("dplyr")
library("tsne")
library("ggfortify")
library("cluster")
library("magrittr")
library("reshape2")
library("corrplot")

```

Load tracking data created by CellProfiler and use cytominer::track to process the data. 
**ToDo: rewrite read images without loop using lapply**.
```{r}
csv_file_name <- 'TrackeddetectedNeutros.csv'
result_dir <- '../../analysis/2017_06_05_tracking/'

strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')
group_cols <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix','TrackObjects_Label_50')

load_data <- function(result_dir, csv_file_name) {
  df <- data_frame()
  for (iDir in list.dirs(result_dir)) {
    file_name <-  file.path(iDir, csv_file_name)
    if (file.exists(file_name)) {
      df <- rbind(df,suppressMessages(read_csv(file_name)))
    }
  }
  return(df)
}
```

The data is loaded as csv file and the data is grouped (needed for extraction of migration features). Additionaly, the Metadta values are corrected (Metadata_condition has two different labels for the same value; We correct it and write "CP" as "CP17" and "SP" as "SP17")
```{r}
population <- load_data(result_dir, csv_file_name) 

population %<>% rename(Metadata_timePoint = Metadata_frame) %>%
  group_by_(.dots = strata) %>%
  arrange(Metadata_timePoint) 
  
population[population == "SP"] <- "SP17"
population[population == "CP"] <- "CP17"
```

The population is reduced to migration experiments that have been performed in FN.  
```{r}
population %<>% 
  filter(Metadata_matrix == 'FN') 
```

The population includes many different parameters including Tracking and Metadata columns. From these columns, only Area-Shape features are normalized.
```{r}
feature_cols_area <-
  colnames(population) %>%
  stringr::str_subset("^Area") %>%
  print

feature_cols_texture <-
  colnames(population) %>%
  stringr::str_subset("^Textu") %>%
  print

feature_cols <- c(feature_cols_area, feature_cols_texture)

```


```{r}
groups <-
  population %>%
  dplyr::select_(.dots = strata) %>%
  dplyr::distinct() %>%
  dplyr::collect()

groups %>% knitr::kable()
```
The data is normalized using cytominer::normalize
* population  the complete data set including controls
* variables columns / features that should be normalized 
* strata  grouping variable. 
* sample  definition of the control group 
```{r}
population %<>% ungroup()

#population %<>% cytominer::generalized_log(population = population, variables = "Texture_AngularSecondMoment_neutrosIlluCorrected_3_0")

normalized <-
  cytominer::normalize(
    population = population,
    variables = feature_cols,
    strata =  'Metadata_id',
    sample = population %>% filter(Metadata_condition == 'control'),
    operation = 'robustize'
  )

normalized %<>% dplyr::collect()

```

All features including NA values are removed (thanks CellProfiler ;)
```{r}
na_frequency <-
  cytominer::count_na_rows(
    population = normalized,
    variables = feature_cols)

na_frequency %>%
  tidyr::gather(feature, na_count) %>%
  knitr::kable()

cleaned <-
  cytominer::select(
    population = normalized,
    variables = feature_cols,
    operation = "drop_na_columns"
)

feature_cols_clean <- c(
  colnames(cleaned) %>%
  stringr::str_subset("^Area"),
    colnames(cleaned) %>%
  stringr::str_subset("^Text")
)
```

The data is log transformed to get a higher Gaussianity.  
```{r}
transformed <-
  cytominer::transform(
    population = cleaned,
    variables = feature_cols_clean
  )

aggregated <-
  cytominer::aggregate(
    population = transformed,
    variables = feature_cols_clean,
    strata = group_cols
  ) %>%
  dplyr::collect()
```

Visualize the results of the log transform.
```{r}

features <- transformed %>% 
  select_(.dots = feature_cols_clean) %>%
  melt()

ggplot(features,aes(x = value)) + 
    facet_wrap(~variable,scales = "free_x") + 
    geom_histogram(bins = 100)
```

```{r}
features <- cleaned %>% 
  select_(.dots = feature_cols_clean) %>%
  melt()

ggplot(features,aes(x = value)) + 
    facet_wrap(~variable,scales = "free_x") + 
    geom_histogram(bins = 100)
```

```{r}
t <-
  cytominer::aggregate(
    population = aggregated,
    variables = feature_cols_clean,
    strata =  c('Metadata_id','Metadata_condition','Metadata_dose')
  ) %>%
  dplyr::collect()

t %<>% mutate(id = paste(Metadata_id, Metadata_condition, Metadata_dose))

 cm <- t %>%
    select(one_of(feature_cols_clean)) %>%
    t %>%
    cor
 
row.names(cm) <- t$id
colnames(cm) <- t$id

 corrplot(cm)
 
 head(t)
```
