---
title: "load_data"
author: "TB"
date: "5/15/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library("tibble")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("purrr")
library("broom")
library("dplyr")
library("tsne")
library("ggfortify")
library("cluster")
library("magrittr")
library("knitr")
library("corrplot")
#library("cytominer")
# load cytominer 

```

# Load data 
The output of CellProfiler track module is loaded as CSV, tracked using cytominer::track and 
stored in the data folder as "track.csv". Once the data is stored, the processing is not repeated;
instead "tracks.csv" is loaded. 
```{r}
csv_in <- 'featureList.csv'
csv_out <- 'tracks.csv'
data_dir <- '../../analysis/2017_atari_sequence/'
strata <- c('experimentID')

if (file.exists(file.path(data_dir, csv_out))) {
  tracks <- read_csv(file.path(data_dir, csv_out))
} else {

  df <- read_csv(file.path(data_dir, csv_in))
  df %<>% dplyr::mutate(Metadata_frame = as.double(Metadata_timePoint)) 
  

  #The data contains tracking data for neutrophils from different conditions. The datasets 
  #can be ditinguished using the Metadata columns defined in strata. 
  track_label = c('TrackObjects_Label')
  
  tracks <- df %>% 
    group_by_(.dots =  c(strata,track_label)) %>%
    arrange(Metadata_timePoint) %>%
    cytominer::track(., c(strata,track_label)) %>%
    group_by_(.dots = strata) 
  }
```


```{r}
write_csv(tracks, file.path(data_dir, csv_out))
```

The quality of the tracking can be assessed using the cytominer::assess function. 
The VOT (valid observation time) column can be used to get a rough estimate of the 
track quality. 
```{r}
tracks %<>% group_by_(.dots = strata)


quality <- cytominer::assess(tracks, 19, strata)

quality %<>% full_join(., 
  tracks %>% 
    filter(Track_Length > 19) %>%
    summarise(mean_xFMI = mean(Track_xFMI)), 
  by = strata)
  
#quality[is.na(quality)] <- 0
quality %>% knitr::kable()
```
Select the experiments with a VOT smaller 0.6. Most of these data sets belong to one ID ("GN0033", ie one human donor)
```{r}
quality %>% 
  filter(VOT < 0.6 ) %>% 
  print

```


```{r}
valid_tracks <- tracks %>%
  filter(Track_Life_Time > 19)

ggplot(data = valid_tracks, aes(Track_Angle)) +
   geom_histogram(binwidth = 0.04)

x <- hist(valid_tracks$Track_Angle, plot = FALSE)

```

```{r}

source("windrose.r")

# angles are scaled to the intervale (-pi, pi)
test_data <- tracks %>%
  filter(Track_Length > 19) %>%
  mutate(Track_Angle = Track_Angle + pi/2) %>% # rotate all angles by 90 degree or pi/2
  mutate(Track_Angle = ifelse(Track_Angle > pi, Track_Angle - 2*pi, Track_Angle) ) %>%
  mutate(Track_Angle = ifelse(Track_Angle < 0, Track_Angle + 2*pi, Track_Angle) )
spdmin <- 0
spdmax <- 16
spdres <- 1
dirres <- 90

spdscale <- 1.5638 # factor to convert speed from pixel / frame to mum / min

h1 <- plot.windrose(spd = spdscale * test_data$Track_Speed, dir = (180 * (test_data$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Migration distribution CP17, all doses")


```
