---
title: "load_data"
author: "TB"
date: "5/15/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library("tibble")
library("dplyr")
library("tidyr")
library("stringr")
library("purrr")
library("magrittr")
library("knitr")
```

# Load data 
The output of CellProfiler track module is loaded as CSV, tracked using cytominer::track and 
stored in the data folder as "track.csv". 
```{r}
csv_in <- 'TrackeddetectedNeutros.csv'
csv_out <- 'clean_tracks.csv'
analysis_folder <- '../../../analysis/2017_04_28_matlab/'
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')

# scale speed from pixel/frame to µm/minute
pixel_size = 0.7819
# frames are recorded each 30 seconds, i.e. 
speed_scale <- pixel_size * 2

# the velocity can be transformed from pixel/frame to µm/minute by multiplying by the factor speed_scale
df <- read_csv(file.path(analysis_folder, csv_in))
df %<>% dplyr::mutate(Metadata_frame = as.double(Metadata_timePoint)) 

#The data contains tracking data for neutrophils from different conditions. The datasets 
#can be ditinguished using the Metadata columns defined in strata. 
track_label = c('TrackObjects_Label')

```
# Cleanup 
Cleanup! Gyde provided a list with frames / videos with an possible technical error. We remove these data.
Gydes list:

09.07.2013 GN0039: Kontrolle - frame 121, 

  * 0,5µM - frame 1 und 2, 
  * 50µM -frame 1-7, 
  * Vehikel - frame 1
  
11.06.2013 GN0033: 

  * 5µm - frame 1-45! Wenn diese frames nicht exkludiert werden können, muss der Tag exkludiert werden
  * 11.07.2013 GN0040: 
  * Kontrolle - frame 1-5, 
  * 0,5µM - 1-7, 
  * 50µm - 1-9

12.07.2013 GN0041: 

  * Kontrolle - 1-10, 
  * 0,5µm- 1-10, 
  * 5µm - 1-10, 
  * 50µm - 1-10

25.04.2013 GN0017: 

  * 0,5µm - frame 1-50!, 
  * 50µm- 1-25!, 
  * Vehikel - 1-25! Wenn diese frames nicht exkludiert werden können, muss der Tag exkludiert werden

15.07.2013 BD0053: 

  * 0,5µm - 1-10, 
  * 5µm - 1-5, 
  * 50µm - 1-5, 
  * Vehikel - 1-5

17.07.2013 BD0054: 

  * Kontrolle - 1-5, 
  * 0,5µm - 1-5, 
  * Vehikel - 1-10

19.07.2013 BD0055: 

  * Kontrolle - 1-10, 
  * 0,5µm - 1-10, 
  * 5µm - 1-5, 
  * 50µm - 1-5

17.09.2013 EJ0005: 

  * 0,5µm - 1-10, 
  * Vehikel HEM - 1, 
  * Vehikel FN - 1-5

18.09.2013 BD0069: 

  * 5µm - 1-5, 
  * 50µm - 1-7, 
  * Vehikel FN - 1-10

19.09.2013 EJ0006: 

  * Vehikel FN - 115-121

20.09.2013 BD0071: 

  * Kontrolle - 1-5, 
  * 0,5µm - 1-5, 
  * Vehikel HEM - 1-10,
  * Vehikel FN - 1-5

26.09.2013 GN0050: 

  * Kontrolle - 1-10, 
  * 50µm - 1-5,   
  * Vehikel HEM - 1-5,
  * Vehikel FN - 1-10

14.11.2013 GN0055: 

  * Kontrolle - 1-25, 
  * 5µm - 1-5, 
  * Vehikel HEM - 1-5

27.09.2013 BD0073: 

  * Kontrolle - 1-5, 
  * 5µm - 1-10, 
  * 50µm - 1-7, 
  * Vehikel HEM- 1-5, 
  * Vehikel FN 1-25! Wenn diese frames nicht exkludiert werden können, hier kein FN vs HEM Vergleich!

30.09.2013 GN0051: 

  * Kontrolle - 1-10, 
  * 5µm - 1-10, 
  * Vehikel HEM - 1-5,
  * Vehikel FN - 1-70! Wenn diese frames nicht exkludiert werden können, hier kein FN vs HEM Vergleich!

03.10.2013 GN0052: 

  * Kontrolle - 1-10, 
  * 5µm - 1-5, 
  * Vehikel HEM - 1-5


Same list in R: 
```{r}
df %<>% select(Metadata_id, Metadata_date, Metadata_matrix, Metadata_condition, Metadata_dose, Metadata_frame, everything())

df1 <- df %>% 
  filter( !((Metadata_id == 'gn0039') & (Metadata_condition == 'control') &  (Metadata_frame == 121) ) ) %>% 
  filter( !((Metadata_id == 'gn0039') & (Metadata_condition == 'vehicle') &  (Metadata_frame == 1) ) ) %>% 
  filter( !((Metadata_id == 'gn0039') & (Metadata_dose == 0.5) &  (Metadata_frame < 3) ) ) %>%
  filter( !((Metadata_id == 'gn0039') & (Metadata_dose == 50) &  (Metadata_frame < 8) ) ) %>% 
  
  filter( !((Metadata_id == 'gn0033') & (Metadata_dose == 5) &  (Metadata_frame < 46) ) ) %>%
  
  filter( !((Metadata_id == 'gn0040') & (Metadata_condition == 'control') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'gn0040') & (Metadata_dose == 0.5) &  (Metadata_frame < 8) ) ) %>%
  filter( !((Metadata_id == 'gn0040') & (Metadata_dose == 50) &  (Metadata_frame < 10) ) ) %>%
  
  filter( !((Metadata_id == 'gn0041') & (Metadata_condition == 'control') & (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'gn0041') & (Metadata_dose == 0.5) &  (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'gn0041') & (Metadata_dose == 5) &  (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'gn0041') & (Metadata_dose == 50) &  (Metadata_frame < 11) ) ) %>%
  
  filter( !((Metadata_id == 'gn0017') & (Metadata_condition == 'vehicle') & (Metadata_frame < 25) ) ) %>%
  filter( !((Metadata_id == 'gn0017') & (Metadata_dose == 0.5) &  (Metadata_frame < 51) ) ) %>%
  filter( !((Metadata_id == 'gn0017') & (Metadata_dose == 50) &  (Metadata_frame < 26) ) ) %>%
  
  filter( !((Metadata_id == 'gn0017') & (Metadata_condition == 'vehicle') & (Metadata_frame < 25) ) ) %>%
  filter( !((Metadata_id == 'gn0017') & (Metadata_dose == 0.5) &  (Metadata_frame < 51) ) ) %>%
  filter( !((Metadata_id == 'gn0017') & (Metadata_dose == 50) &  (Metadata_frame < 26) ) ) %>%
  
  filter( !((Metadata_id == 'bd0053') & (Metadata_condition == 'vehicle') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'bd0053') & (Metadata_dose == 0.5) &  (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'bd0053') & (Metadata_dose == 5) &  (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'bd0053') & (Metadata_dose == 50) &  (Metadata_frame < 6) ) ) %>%
  
  filter( !((Metadata_id == 'bd0054') & (Metadata_condition == 'control') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'bd0054') & (Metadata_condition == 'vehicle') & (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'bd0054') & (Metadata_dose == 0.5) &  (Metadata_frame < 6) ) ) %>%
  
  filter( !((Metadata_id == 'bd0054') & (Metadata_condition == 'control') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'bd0054') & (Metadata_condition == 'vehicle') & (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'bd0054') & (Metadata_dose == 0.5) &  (Metadata_frame < 6) ) ) %>%
  
  filter( !((Metadata_id == 'bd0055') & (Metadata_condition == 'control') & (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'bd0055') & (Metadata_dose == 0.5) &  (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'bd0055') & (Metadata_dose == 5) &  (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'bd0055') & (Metadata_dose == 50) &  (Metadata_frame < 6) ) ) %>%
  
  filter( !((Metadata_id == 'bd0055') & (Metadata_condition == 'control') & (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'bd0055') & (Metadata_dose == 0.5) &  (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'bd0055') & (Metadata_dose == 5) &  (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'bd0055') & (Metadata_dose == 50) &  (Metadata_frame < 6) ) ) %>%
  
  filter( !((Metadata_id == 'ej0005') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'HEM') & (Metadata_frame < 2) ) ) %>%
  filter( !((Metadata_id == 'ej0005') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'FN') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'ej0005') & (Metadata_dose == 0.5) &  (Metadata_frame < 11) ) ) %>%
  
  filter( !((Metadata_id == 'bd0069') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'FN') & (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'bd0069') & (Metadata_dose == 5) &  (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'bd0069') & (Metadata_dose == 50) &  (Metadata_frame < 8) ) ) %>%
  
  filter( !((Metadata_id == 'ej0006') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'FN') & (Metadata_frame > 114) ) ) %>%
  
  filter( !((Metadata_id == 'bd0071') & (Metadata_condition == 'control') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'bd0071') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'HEM') & (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'bd0071') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'FN') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'bd0071') & (Metadata_dose == 0.5) &  (Metadata_frame < 6) ) ) %>%
  
  filter( !((Metadata_id == 'gn0050') & (Metadata_condition == 'control') & (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'gn0050') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'HEM') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'gn0050') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'FN') & (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'gn0050') & (Metadata_dose == 50) &  (Metadata_frame < 6) ) ) %>%
  
  filter( !((Metadata_id == 'gn0055') & (Metadata_condition == 'control') & (Metadata_frame < 26) ) ) %>%
  filter( !((Metadata_id == 'gn0055') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'HEM') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'gn0055') & (Metadata_dose == 5) &  (Metadata_frame < 6) ) ) %>%
  
  filter( !((Metadata_id == 'bd0073') & (Metadata_condition == 'control') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'bd0073') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'HEM') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'bd0073') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'FN') & (Metadata_frame < 26) ) ) %>%
  filter( !((Metadata_id == 'bd0073') & (Metadata_dose == 5) &  (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'bd0073') & (Metadata_dose == 50) &  (Metadata_frame < 8) ) ) %>%
  
  filter( !((Metadata_id == 'gn0051') & (Metadata_condition == 'control') & (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'gn0051') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'HEM') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'gn0051') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'FN') & (Metadata_frame < 71) ) ) %>%
  filter( !((Metadata_id == 'gn0051') & (Metadata_dose == 5) &  (Metadata_frame < 11) ) ) %>%
  
  filter( !((Metadata_id == 'gn0052') & (Metadata_condition == 'control') & (Metadata_frame < 11) ) ) %>%
  filter( !((Metadata_id == 'gn0052') & (Metadata_condition == 'vehicle') & (Metadata_matrix == 'HEM') & (Metadata_frame < 6) ) ) %>%
  filter( !((Metadata_id == 'gn0052') & (Metadata_dose == 5) &  (Metadata_frame < 6) ) ) %>%
  
  print
```
## Track
cytominer::track is used to create trajetories and compute migration parameters 
```{r}
tracks <- df1 %>% 
  ungroup() %>%
  group_by_(.dots =  c(strata,track_label)) %>%
  arrange(Metadata_timePoint) %>%
  cytominer::track(., c(strata,track_label)) %>%
  group_by_(.dots = strata) %>% 
  print()

tracks %>% select(Track_Angle) %>% print
```

## PostProcessing 

Calculate speed in µm/minute
```{r}
postprocessed <- tracks %>%
  mutate(Track_Speed = Track_Speed * speed_scale) %>%
  mutate(Track_Speed_max = Track_Speed_max * speed_scale) %>%
  mutate(Track_Speed_X = Track_Speed_X * speed_scale) %>%
  mutate(Track_Speed_Y = Track_Speed_Y * speed_scale) %>%
  mutate(Track_Distance_Traveled = pixel_size * Track_Distance_Traveled) %>%
  mutate(Track_Integrated_Distance_Traveled = pixel_size * Track_Integrated_Distance_Traveled) 
```

All na values are set to 'None' and all tracks are stored 
```{r}
postprocessed$Metadata_dose[is.na(postprocessed$Metadata_dose)] <- 'None'
write_csv(postprocessed, file.path(analysis_folder, csv_out))
```
