---
title: "03-data_visualization"
author: "TB"
date: "7/19/2017"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library("tibble")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("r2excel")
```

# Load data
We load the clean tracks and export 
* xFMI
* Speed and 
* directionality
as histogram plots to pdf files. 

Helpfull 

https://stackoverflow.com/questions/27556707/applying-a-function-to-the-output-of-dplyrs-group-by
https://stackoverflow.com/questions/29034863/apply-a-ggplot-function-per-group-with-dplyr-and-set-title-per-group

```{r}
csv_in <- 'clean_tracks.csv'
analysis_folder <- '../../../analysis/2017_04_28_matlab/'
export_folder <- '../../../analysis/2017_04_28_matlab/4gyde/'
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')

population <- read_csv(file.path(analysis_folder,csv_in)) %>% 
  filter(Track_One_Cell == 1) %>%
  mutate(ID = str_c(Metadata_id, Metadata_condition, Metadata_dose, Metadata_matrix, sep = ' ')) %>%
  mutate(Metadata_condition = replace(Metadata_condition, Metadata_condition == "water", "vehicle")) %>%
  mutate(Track_Valid = Track_Length > 19) %>% 
  mutate(Track_Valid = as.numeric(Track_Valid)) %>% 
  print

  sem <- function(x){
  sd(x) / sqrt(length(x))
}

```


# Export Trajectories 
Test: We export all trajectories as csv. Each experiment is exported separetly. This code is not used. Instead, we use the r2excel package to write the data on different sheeds.
```{}
df <- population %>% 
  filter(Track_Length > 19) %>%
  ungroup() %>%
  group_by(ID) %>%
  arrange(Track_Sector) %>%
  select(ID, Track_Speed, Track_Directionality, Track_xFMI, Track_yFMI, Track_Sector, Track_Angle, Track_Length, TrackObjects_Label)

dl = split(df, df$ID) 
for (somegroup in dl) {write.csv(select(somegroup, -ID), file.path(analysis_folder,str_c('tracks ',first(somegroup$ID), ".csv")))}
```


# rename track sectors
```{r}
population %<>% 
  mutate(Track_Sector = replace(Track_Sector, Track_Sector == 1, "positive sector")) %>%
  mutate(Track_Sector = replace(Track_Sector, Track_Sector == 2, "negative sector")) %>%
  mutate(Track_Sector = replace(Track_Sector, Track_Sector == 3, "neutral sector (up)")) %>%
  mutate(Track_Sector = replace(Track_Sector, Track_Sector == 4, "neutral sector (down)")) 
```

# calculate freaction of trajectories in each sector 
```{r}
valid_tracks <- population %>% 
  group_by(ID,Track_Sector) %>%
  na.omit() %>%
  summarise(Fraction_valid_tracks = sum(Track_Valid) / n()) %>% 
  print

valid_tracks_all <- population %>% 
  group_by(ID) %>%
  na.omit() %>%
  summarise(Fraction_valid_tracks = sum(Track_Valid) / n()) %>% 
  mutate(Track_Sector = "all") %>%
select(ID, Track_Sector, everything()) %>%
  print

valid_tracks <- bind_rows(valid_tracks,valid_tracks_all) %>% 
  ungroup() %>%
  group_by(ID) %>% print
```
# summarize and export speed 
* calcuate mean, sd and sem for neutros in all sectors 
* and for each sector seperately 
```{r}
speed <- population %>% 
  filter(Track_Length > 19) %>%
  group_by(ID,Track_Sector) %>%
  na.omit() %>%
  summarise(Mean = mean(Track_Speed), 
            SD = sd(Track_Speed), 
            SEM = sem(Track_Speed), 
            n = n())


speed_all <- population %>% 
  filter(Track_Length > 19) %>%
  group_by(ID) %>%
  na.omit() %>%
  summarise(Mean = mean(Track_Speed), 
            SD = sd(Track_Speed), 
            SEM = sem(Track_Speed), 
            n = n())  %>%
  mutate(Track_Sector = 'all') %>%
  select(ID, Track_Sector, everything()) 
  

speed2 <-  bind_rows(speed, speed_all) %>% 
  group_by(ID, Track_Sector) %>% 
  left_join(., valid_tracks, by = c("ID","Track_Sector")) %>% 
  group_by(ID) %>% 
  arrange(ID, Track_Sector)

write_csv(speed2, file.path(analysis_folder, 'speed.csv'))
```
 
# summarize and export directionality
```{r}
directionality <- population %>% 
  filter(Track_Length > 19) %>%
  group_by(ID,Track_Sector) %>%
  na.omit() %>%
  summarise(Mean = mean(Track_Directionality), 
            SD = sd(Track_Directionality), 
            SEM = sem(Track_Directionality), 
            n = n())  


directionality_all <- population %>% 
  filter(Track_Length > 19) %>%
  group_by(ID) %>%
  na.omit() %>%
  summarise(Mean = mean(Track_Directionality), 
            SD = sd(Track_Directionality), 
            SEM = sem(Track_Directionality), 
            n = n())  %>%
  mutate(Track_Sector = 'all') %>%
  select(ID, Track_Sector, everything()) 
  

directionality2 <-  bind_rows(directionality, directionality_all) %>% 
  group_by(ID, Track_Sector) %>% 
  left_join(., valid_tracks, by = c("ID","Track_Sector")) %>% 
  group_by(ID) %>% 
  arrange(ID, Track_Sector) 
 
write_csv(directionality2, file.path(analysis_folder, 'directionality.csv'))
```
```{r}
df <- population %>% 
  filter(Track_Length > 19) %>% 
  select(ID, Track_Speed, Track_Directionality, Track_xFMI, Track_yFMI, Track_Sector, Track_Angle, Track_Length, TrackObjects_Label) %>%
  ungroup() %>%
  group_by(ID) %>%
  arrange(Track_Sector) 

ids <- df %>% 
  select(ID) %>%
  ungroup() %>%
  group_by(ID) %>%
  slice(1)

ids <- as.vector(ids$ID)

for (id in ids) {
  track_export <- df %>%
    filter(ID == id) %>%
    ungroup()
  
  speed_export <- speed2 %>%
    filter(ID == id) %>%
    ungroup()
  
  directionality_export <- directionality2 %>%
    filter(ID == id) %>%
    ungroup()
  
  file_name <- file.path(export_folder,str_c(id,'.xlsx',sep = ""))

  xlsx.writeMultipleData(file_name, track_export, speed_export, directionality_export)
}
```



```{r}
population %>% 
  filter(Track_Length > 20) %>%
  filter(Metadata_matrix == "FN") %>%
  filter(Metadata_condition  == "CP17") %>%
  filter(Metadata_dose == "50") %>%
  ggplot(data = .) +
    aes(x = Track_Speed) +
    geom_histogram(binwidth = 0.3)
```


Data visualization 

``` {r}
population %>%
  mutate(ID = str_c( Metadata_condition, Metadata_dose, sep = '_')) %>%
  ggplot(data=.) + 
    aes(x = Track_Speed) +
    geom_histogram() +
    facet_wrap(Metadata_id ~ ID,scales = "free")
  
```


Save all plots for Gyde!
```{}
population %>%
  ungroup() %>%
  group_by(Metadata_id, Metadata_condition, Metadata_dose) %>%
  do({
  p <- ggplot(., aes(x=Track_Speed)) + geom_histogram() + ggtitle(str_c(unique(.$Metadata_id),unique(.$Metadata_condition,.),unique(.$Metadata_dose),sep=' '))
  ggsave(p, filename=str_c('speed_',unique(.$Metadata_id),unique(.$Metadata_condition),unique(.$Metadata_dose),".pdf",sep = '_'))
  })

population %>%
  ungroup() %>%
  group_by(Metadata_id, Metadata_condition, Metadata_dose) %>%
  do({
  p <- ggplot(., aes(x=Track_xFMI)) + geom_histogram() + ggtitle(str_c(unique(.$Metadata_id),unique(.$Metadata_condition,.),unique(.$Metadata_dose),sep=' '))
  ggsave(p, filename=str_c('xfmi_',unique(.$Metadata_id),unique(.$Metadata_condition),unique(.$Metadata_dose),".pdf",sep = '_'))
  })


population %>%
  ungroup() %>%
  group_by(Metadata_id, Metadata_condition, Metadata_dose) %>%
  do({
  p <- ggplot(., aes(x=Track_Directionality)) + geom_histogram() + ggtitle(str_c(unique(.$Metadata_id),unique(.$Metadata_condition,.),unique(.$Metadata_dose),sep=' '))
  ggsave(p, filename=str_c('directionality_',unique(.$Metadata_id),unique(.$Metadata_condition),unique(.$Metadata_dose),".pdf",sep = '_'))
  })
```