---
title: "load_data"
author: "TB"
date: "07/07/2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("magrittr")
```


# Load data 
Load tracking data created using MATLAB as normalized and not normalized data. 

The normalization was performed using cytominer::normalize and the following variables 
are normalized: 
* "Track_Speed",
* "Track_Speed_Y",
* "Track_Speed_X",
* "Track_xFMI",
* "Track_yFMI",
* "Track_Directionality",
* "Track_Distance_Traveled", 
* "Track_CI"


```{r}
csv_tracks <- 'clean_tracks.csv'
csv_normalized <- 'clean_normalized.csv'

analysis_folder <- '/Users/tbecker/Documents/2017_05_10_neutrophile_inhibitor/workspace/analysis/2018_fmlp'

# grouping variable
strata <- c('Metadata_condition','Metadata_dose','Metadata_id',
            'Metadata_date','Metadata_matrix','Metadata_chemokine')


```

# load data 
We load the data and
* update the Metadata for one experiment
* remove short trajectories 
```{r} 
population <- read_csv(file.path(analysis_folder, csv_tracks)) %>%
  mutate(Metadata_condition = replace(Metadata_condition, Metadata_condition == "water", "vehicle")) %>%
  filter(Track_Length > 19) %>%
  mutate(Metadata_dose = ifelse(is.na(Metadata_dose), "none", Metadata_dose))

population %>% select(Track_Speed) %>% print
```

We define the variables for normalization and use cytominer::normalize
```{r}
feature_var = c("Track_Speed","Track_Speed_Y","Track_Speed_X","Track_xFMI","Track_yFMI","Track_Directionality","Track_Distance_Traveled","Track_CI")

# optionally we can run 
#population <- cytominer::generalized_log(population, variables = feature_var)

normalized <-
  cytominer::normalize(
    population = population,
    variables = feature_var,
    strata =  "Metadata_id",
    sample = population %>% filter(Metadata_condition == "vehicle"),
    operation = "standardize"
  )

normalized %<>% dplyr::collect() 

normalized %>% select(Track_Speed) %>% print

```

## Save normalized data.
```{r}
write_csv(normalized, file.path(analysis_folder, csv_normalized))
```

```{r}
sem <- function(x){
  print(x)
  sem <- 
    print(sem)
  return(sem)

}

results <- normalized %>% 
  group_by(Metadata_dose, Metadata_condition) %>% 
  summarise(
    n = n(),
    mean_speed = mean(Track_Speed),
    sem_speed = sd(Track_Speed) / sqrt(n()),
    sd_speed = sd(Track_Speed),
    mean_directionality  = mean(Track_Directionality),
#    sem_directionality = sd(Track_Directionality) / sqrt(Track_Directionality),
    sd_directionality = sd(Track_Directionality),
    mean_xfmi = mean(Track_xFMI),
#    sem_xfmi = sd(Track_xFMI) / sqrt(Track_xFMI),
    sd_xfmi = sd(Track_xFMI)
    ) %>% print

write_csv(results, file.path(analysis_folder,'results.csv'))

```
```{r}
# to change number of lines see 
# https://stackoverflow.com/questions/24845652/specifying-the-scale-for-the-density-in-ggplot2s-stat-density2d
ggplot( data = population %>% filter(Metadata_dose != 50)) +  
  aes(x = Track_Speed, y = Track_Directionality, color = Metadata_condition) + 
  geom_point() + 
  facet_wrap( ~ Metadata_id)

normalized %>% 
  group_by(Metadata_condition, Metadata_id) %>%
  summarise(mean_speed = median(Track_Speed) ) %>%
  print
  
```
```{r}
results_per_id <- normalized %>% 
  group_by(Metadata_id, Metadata_condition, Metadata_dose) %>% 
  summarise(
    n = n(),
    mean_speed = mean(Track_Speed),
    sem_speed = sd(Track_Speed) / sqrt(n()),
    sd_speed = sd(Track_Speed),
    mean_directionality  = mean(Track_Directionality),
    sem_directionality = sd(Track_Directionality) / sqrt(n()),
    sd_directionality = sd(Track_Directionality),
    mean_xfmi = mean(Track_xFMI),
    sem_xfmi = sd(Track_xFMI) / sqrt(n()),
    sd_xfmi = sd(Track_xFMI)
    ) %>% print

```


```{r}
ggplot(data = results_per_id) + 
  aes(x = mean_speed, y = mean_xfmi, color = Metadata_dose, shape = as.factor(Metadata_id) ) + 
  geom_point()
```

