---
title: "load_data"
author: "TB"
date: "07/07/2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("magrittr")
```


# Load data 
Load tracking data created using MATLAB as normalized and not normalized data. 

The normalization was performed using cytominer::normalize and the following variables 
are normalized: 
* "Track_Speed",
* "Track_Speed_Y",
* "Track_Speed_X",
* "Track_xFMI",
* "Track_yFMI",
* "Track_Directionality",
* "Track_Distance_Traveled", 
* "Track_CI"


```{r}
csv_tracks <- 'clean_tracks.csv'
csv_normalized <- 'clean_normalized.csv'

analysis_folder <- '/Users/tbecker/Documents/2017_05_10_neutrophile_inhibitor/workspace/analysis/2018_ltb4'

# grouping variable
strata <- c('Metadata_condition','Metadata_dose','Metadata_id',
            'Metadata_date','Metadata_matrix','Metadata_chemokine')


```

# load data 
We load the data and
* update the Metadata for one experiment
* remove short trajectories 
```{r} 
population <- read_csv(file.path(analysis_folder, csv_normalized)) %>%
  mutate(Metadata_condition = replace(Metadata_condition, Metadata_condition == "water", "vehicle")) %>%
  filter(Track_Length > 19)
```
```{r}
population %>% select(Metadata_id, Metadata_condition, Metadata_dose) %>% 
  group_by(Metadata_id) %>% 
  summarise(n = n())
```