---
title: "load_data"
author: "TB"
date: "5/15/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
```


# Load data 
## load tracks 
```{r}
csv_in <- 'clean_tracks.csv'
analysis_folder <- '../../../analysis/2017_04_28_matlab/'
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')

df <- read_csv(file.path(analysis_folder,csv_in)) %>% 
  group_by_(.dots = strata)
```
# load single cell data
```{r}
single_cell_data <- 'TrackeddetectedNeutros.csv'
cells <- read_csv(file.path(analysis_folder, single_cell_data)) 

cells$Metadata_dose[is.na(cells$Metadata_dose)] <- 'None'

cells %>% mutate(Metadata_dose = as.double(Metadata_dose))
  
```

quick check how the cp tracked data looks like
```{r}
population_cp <- read_csv("../../../analysis/2017_morph_gradient_3/tracks_cp.csv")

population_cp %>% select(Track_Speed) %>% arrange(-Track_Speed) %>% print
```

```{r}
population <- df %>% filter(Track_Length > 1, Track_Life_Time > 1)

```

The fastest cells 
```{r}
df_fast_tracks <- population %>% 
  select_(.dots = c(strata, "Track_Speed","TrackObjects_Label", "Track_One_Cell", "Track_Length", "Track_Life_Time")) %>%
  filter(Track_One_Cell) %>%
  filter(Track_Life_Time > 19) %>%
  ungroup() %>%
  arrange(-Track_Speed) %>%
  slice(1:100) %>%
  print
```

Now we check single cells
```{r}

df_fast_cell <- right_join(cells, df_fast_tracks, by = c(strata, 'TrackObjects_Label')) %>%
  select(Metadata_id, Metadata_matrix, Metadata_condition, Metadata_dose, Track_Length, Track_Life_Time, TrackObjects_Label, everything()) %>%
  print
```
The tracks with a high speed consists of two different paths. Specially the experiment with id = GN0055 has several fast cells.
Example: 
* gn0055, HEM, CP17, 5, TrackObjects_Label 28. 
* Track_Length and Track_Life_Time are 3 but the current track has 7 entries in frames c(1,3,4,5,6,21,22)  

We load the single cell information extracted using MATLAB and check whats going on. 
```{r}
df_single_cells <- read.csv('/Users/tbecker/Documents/2017_03_08_neutrophile_migration_becker/2017_04_05_CP17/images/CP17_HEM/260913 gn0050 cp17 in hem/gn0050_hem_il8_cp17_5/results/featureList.csv')

df_single_cells %>% filter(TrackObjects_Label == 28) %>% print

```
The single cell data looks good. 

Next step: check how the single cell data of all experiments are collected

One error: file 
Metadata_complete had an error:
* control experiment of gn0055 had the wrong metadata, it was tracked as CP17 with dose = 5. As a result we had tracks with the same id! 
* check file track_and_export_matlab.Rmd in the 2017_03
* tracked_neutros %>% filter(Metadata_matrix == "HEM", Metadata_id == "gn0055",TrackObjects_Label == 28) %>% print()   