---
title: "load_data"
author: "TB"
date: "07/07/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("magrittr")
source("../multiplot.r")
```
# How does different normalization schemes affect our tracking data 
This notebooks compares tracking data normalization using different methods and using different control groups.

Our data set consists of cell tracking data run with different conditions.

Each time series characterizes the chemotaxis of neutrophils in an in vitro assay. In the analysed experiments the chemoattractant interleukin 8 was used to create an gradient that directs from the left border of the images / channel to the left channel.
For each patient or experiment id ("Metadata_id") a set of five (FN) or six (HEM) time series were recorded consisting of 
* one control run, "Metadata_condition" = "control"
* one vehicle run, "Metadata_condition" = "vehicle"
* three runs with "Metadata_condition" "CP17" or "SP17" in with different doses Metadata_dose = c(0.5, 5, 50)

The experiments for each patient are either run in the matrix HEM or FN specified as "Metadata_matrix" = "FN" or "HEM". For all patients that have been run in HEM, one additional run with "Metadata_condition" = "vehicle" was run using the matrix "FN". 

Given these data we normalize all runs that belong to one patient on three different ways:
1. Experiments are normalized using the control group 
2. Experiments are normalized using the vehicle group of the corredpsonding matrix. 
3. Experiemnts are normlaized using the vehicle gorup using matrix FN. 

Normalization 3 makes it possible to compare the different experiments run in different matrices. 

# Load data 
Load tracking data created using MATLAB as normalized and not normalized data. 

```{r}
csv_tracks <- 'clean_tracks.csv'
csv_normalized <- 'clean_normalized.csv'
analysis_folder <- '../../../analysis/2017_04_28_matlab/'
```

Experiments are groupes by condition, dose, id, data and matrix
```{r}
# grouping variables 
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')
```

Read the csv
```{r} 
df <- read_csv(file.path(analysis_folder, csv_tracks)) %>%
  filter(Track_Length > 19) 
  # filter(Metadata_id != "ej0005") %>%
  # filter(Metadata_id != "bd0069")
```

All IDs run in HEM and in FN
```{r}
df_id_matrix <- df %>%
  filter(Metadata_condition == "control") %>%
  select(Metadata_id, Metadata_matrix) %>%
  group_by(Metadata_id) %>%
  slice(1) %>%
  print
```

We define the variables for normalization 
```{r}
feature_var = c("Track_Speed","Track_Speed_Y","Track_Speed_X","Track_xFMI","Track_yFMI","Track_Directionality","Track_Distance_Traveled","Track_CI")
```
# optionally we can run 

```{}
population <- cytominer::generalized_log(population, variables = feature_var)
```

```{r}
population <- df 
#%>% filter(Track_Sector %in% c(1,2) )
```

# normalize against control group

```{r}
# define control group
sample <- population %>% filter(Metadata_condition == "control") 
  

normalized <-
  cytominer::normalize(
    population = population,
    variables = feature_var,
    strata =  "Metadata_id",
    sample = sample,
    operation = "standardize"
  ) 

# collapse data to single experiments 
experiments <- 
  cytominer::aggregate(
    population = normalized,
    variables = feature_var,
    strata  = c("Metadata_matrix","Metadata_id", "Metadata_condition", "Metadata_dose"),
    operation = "mean" 
  )

dose <- 
  cytominer::aggregate(
    population = normalized,
    variables = feature_var,
    strata  = c("Metadata_matrix","Metadata_dose","Metadata_condition"),
    operation = "mean" 
  )

```

```{r}
p1 <- ggplot(data = experiments %>%  
    filter(Metadata_matrix == "FN")) + 
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

p2 <- ggplot(data = dose %>%  
    filter(Metadata_matrix == "FN")) +
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

p3 <- ggplot(data = experiments %>%  
    filter(Metadata_matrix == "HEM") ) + 
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

p4 <- ggplot(data = dose %>%  
    filter(Metadata_matrix == "HEM")) +
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

multiplot(p1, p2, p3, p4, cols=1)
```


# normalize against vehicle group

```{r}
# define control group
id_hem <- df_id_matrix %>%
  filter(Metadata_matrix == "HEM") %>%
  extract2("Metadata_id") %>% 
  print 

```
```{r}
sample <- population %>% 
  filter(Metadata_condition == "vehicle") %>%
  filter( !((Metadata_id %in% id_hem) & (Metadata_matrix == "FN") ))

population2 <-  population %>% 
  filter( !((Metadata_id %in% id_hem) & (Metadata_matrix == "FN") ))

sample %>% select(Metadata_matrix, Metadata_id) %>% group_by(Metadata_id, Metadata_matrix) %>% slice(1) %>% print
```  
```{r}
normalized <-
  cytominer::normalize(
    population = population2,
    variables = feature_var,
    strata =  "Metadata_id",
    sample = sample,
    operation = "standardize"
  )  %>% 
  filter(Metadata_dose %in% c(5,50))

# collapse data to single experiments 
experiments <- 
  cytominer::aggregate(
    population = normalized,
    variables = feature_var,
    strata  = c("Metadata_matrix","Metadata_id", "Metadata_condition", "Metadata_dose"),
    operation = "mean" 
  )

dose <- 
  cytominer::aggregate(
    population = normalized,
    variables = feature_var,
    strata  = c("Metadata_matrix","Metadata_dose","Metadata_condition"),
    operation = "mean" 
  )

```

```{r}
normalized %>% 
  group_by(Metadata_condition, Metadata_dose, Metadata_matrix, Metadata_id) %>% 
  filter(Metadata_dose == 5, Metadata_condition == "SP17") %>%
  summarise(mean_speed = mean(Track_Speed))

p1 <- ggplot(data = experiments %>%  
    filter(Metadata_matrix == "FN")
  ) + 
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

p2 <- ggplot(data = dose %>%  
    filter(Metadata_matrix == "FN")) +
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

p3 <- ggplot(data = experiments %>%  
    filter(Metadata_matrix == "HEM") ) + 
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

p4 <- ggplot(data = dose %>%  
    filter(Metadata_matrix == "HEM")) +
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

multiplot(p1, p2, p3, p4, cols=1)
```



# normalize against vehicle / FN

```{r}
# define control group
sample <- population %>% filter(Metadata_condition == "vehicle", Metadata_matrix == "FN")

normalized <-
  cytominer::normalize(
    population = population %>% filter(Metadata_id != "bd0055"),
    variables = feature_var,
    strata =  "Metadata_id",
    sample = sample,
    operation = "standardize"
  ) 

# collapse data to single experiments 
experiments <- 
  cytominer::aggregate(
    population = normalized,
    variables = feature_var,
    strata  = c("Metadata_matrix","Metadata_id", "Metadata_condition", "Metadata_dose"),
    operation = "mean" 
  )

dose <- 
  cytominer::aggregate(
    population = normalized,
    variables = feature_var,
    strata  = c("Metadata_matrix","Metadata_dose","Metadata_condition"),
    operation = "mean" 
  )
```
```{r}
p1 <- ggplot(data = experiments %>%  
    filter(Metadata_matrix == "FN")) + 
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

p2 <- ggplot(data = dose %>%  
    filter(Metadata_matrix == "FN")) +
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

p3 <- ggplot(data = experiments %>%  
    filter(Metadata_matrix == "HEM") ) + 
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

p4 <- ggplot(data = dose %>%  
    filter(Metadata_matrix == "HEM")) +
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

multiplot(p1, p2, p3, p4, cols=1)
```
# Not normalized at all 

```{r}
# collapse data to single experiments 
experiments <- 
  cytominer::aggregate(
    population = population,
    variables = feature_var,
    strata  = c("Metadata_matrix","Metadata_id", "Metadata_condition", "Metadata_dose"),
    operation = "mean" 
  )

dose <- 
  cytominer::aggregate(
    population = population,
    variables = feature_var,
    strata  = c("Metadata_matrix","Metadata_dose","Metadata_condition"),
    operation = "mean" 
  )
```

```{r}
p1 <- ggplot(data = experiments %>%  
    filter(Metadata_matrix == "FN")) + 
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose, geom_tile("FN") )  +
  geom_point()

p2 <- ggplot(data = dose %>%  
    filter(Metadata_matrix == "FN")) +
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point() 

p3 <- ggplot(data = experiments %>%  
    filter(Metadata_matrix == "HEM") ) + 
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point() 

p4 <- ggplot(data = dose %>%  
    filter(Metadata_matrix == "HEM")) +
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point() 

multiplot(p1, p2, p3, p4, cols=1)

```


