---
title: "Data analysis published in 'CP17 in neutrophile migration'"
author: "Tim Becker"
date: "8/30/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
source("../windrose.r")
library("magrittr")
```

# Input data 
* The tracking data is stored in the file clean_tracks.csv.
* The normalized data is stored in the file clean_normalized.csv. Normalization can be found in 04_normalize.Rmd

```{r}
csv_tracks <- 'clean_tracks.csv'
csv_normalized <- 'clean_normalized.csv'
analysis_folder <- '../../../analysis/2017_04_28_matlab/'
```


Definition of the grouping variables. 
```{r}
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')


```

Tracking and normalized data is loaded as a data frame, sorted and ordered 
```{r}
tracks <- read_csv(file.path(analysis_folder, csv_tracks)) %>%
  select(Metadata_id,Metadata_matrix, Metadata_condition, Metadata_dose, everything() ) %>%
  arrange(Metadata_id, Metadata_matrix, Metadata_condition, Metadata_dose) %>%
  group_by_(.dots = strata) %>%
  filter(Track_Length > 19)

normalized <- read_csv(file.path(analysis_folder, csv_normalized)) %>%
  select(Metadata_id,Metadata_matrix, Metadata_condition, Metadata_dose, everything() ) %>%
  arrange(Metadata_id, Metadata_matrix, Metadata_condition, Metadata_dose) %>%
  group_by_(.dots = strata)  %>%
  filter(Track_Length > 19)

```

```{r}
group_cp17 <- tracks %>% 
  filter(Metadata_condition == "CP17") %>%
  ungroup() %>% 
  group_by(Metadata_id) %>% 
  slice(1) %>%
  extract2("Metadata_id") %>% 
  print

group_sp17 <- tracks %>% 
  filter(Metadata_condition == "SP17") %>%
  ungroup() %>% 
  group_by(Metadata_id) %>% 
  slice(1) %>%
  extract2("Metadata_id") %>% 
  print

```


```{r}
tracks %>% ungroup %>% filter(Metadata_matrix == "FN") %>% filter(Metadata_condition == "vehicle") %>% summarise(mean_displacement = mean(Track_Distance_Traveled))

normalized %>% 
  filter(Metadata_matrix == "FN") %>% 
  mutate(Slow = Track_Distance_Traveled < 0.2) %>% 
  ungroup() %>% 
  group_by(Metadata_condition) %>% 
  summarise(n_slow = sum(Slow), fraction = sum(Slow) / n()) 

```

```{r}
normalized %>% filter(Metadata_condition == "vehicle", Metadata_matrix == "FN") %>% ggplot(data = ., aes(x=Track_xFMI)) +
  geom_histogram(bins = 50)

```

 Next we rotate the angle by 90 degrees and transform the speed from µm/min to µm/sec
```{r}
 population <- tracks %>% 
  filter(Track_Length > 19) %>%
  mutate(Track_Angle = Track_Angle + pi/2) %>% # rotate all angles by 90 degree or pi/2
  mutate(Track_Angle = ifelse(Track_Angle > pi, Track_Angle - 2*pi, Track_Angle) ) %>%
  mutate(Track_Angle = ifelse(Track_Angle < 0, Track_Angle + 2*pi, Track_Angle) ) %>%
  mutate(Track_Speed = Track_Speed / 60)
``` 

Show all groups that are analyzed 

```{r}
normalized %>% 
  ungroup() %>%
  group_by_(.dots = strata) %>%
  slice(1) %>%
  group_by_(.dots =  c('Metadata_matrix','Metadata_condition','Metadata_dose','Metadata_id')) %>% 
  summarise( n = n()) %>%
  knitr::kable(
)
```

Angle distribution of trajectories for all migration run in HEM. 

```{r}
test_data <- population %>%
  filter(Metadata_matrix == "HEM") %>%
  filter(Metadata_id != "bd0055")

CP17 <- test_data %>% 
  filter(Metadata_condition == "CP17") %>%
  filter(Metadata_dose == 5) 
  
SP17 <- test_data %>% 
  filter(Metadata_condition == "SP17") %>%
  filter(Metadata_dose == 5) 
  
controls <- test_data %>% 
  filter(Metadata_condition == "control") 

vehicle <- test_data %>% 
  filter(Metadata_condition == "vehicle") 

spdmin <- 0
spdmax <- 0.3
spdres <- 0.02
dirres <- 90

h1 <- plot.windrose(spd = CP17$Track_Speed, dir = (180 * (CP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle distribution for migration  in FN (CP17, 50µm)")

h2 <- plot.windrose(spd = SP17$Track_Speed, dir = (180 * (SP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle distribution for migration  in FN (SP17, 50µm)")

h3 <- plot.windrose(spd = controls$Track_Speed, dir = (180 * (controls$Track_Angle) / pi),
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle distribution for migration in FN (control)")

h4 <- plot.windrose(spd = vehicle$Track_Speed, dir = (180 * (vehicle$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres,  title_name = "Angle distribution for migration in FN (vehicle) ")
```

Angle distribution of trajectories for all migration run in HEM. 

```{r}
test_data <- population %>%
  filter(Metadata_matrix == "HEM") 

CP17 <- test_data %>% 
  filter(Metadata_condition == "CP17") %>%
  filter(Metadata_dose == 5) 
  
SP17 <- test_data %>% 
  filter(Metadata_condition == "SP17") %>%
  filter(Metadata_dose == 5) 
  
controls <- test_data %>% 
  filter(Metadata_condition == "control") 

vehicle <- test_data %>% 
  filter(Metadata_condition == "vehicle") 

spdmin <- 0
spdmax <- 0.3
spdres <- 0.02
dirres <- 10

h1 <- plot.windrose(spd = CP17$Track_Speed, dir = (180 * (CP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle distribution for migration  in FN (CP17, 50µm)")

h2 <- plot.windrose(spd = SP17$Track_Speed, dir = (180 * (SP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle distribution for migration  in FN (SP17, 50µm)")

h3 <- plot.windrose(spd = controls$Track_Speed, dir = (180 * (controls$Track_Angle) / pi),
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle distribution for migration in FN (control)")

h4 <- plot.windrose(spd = vehicle$Track_Speed, dir = (180 * (vehicle$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres,  title_name = "Angle distribution for migration in FN (vehicle) ")
```
How does the speed differ for migrations run in FN or HEM? We compare the speed of all experiments with an induced chemotaxis (vehicle).
```{r}
ggplot(data = population %>% filter(Metadata_condition == "vehicle"), aes(x = Metadata_matrix, y = Track_Speed)) + 
  geom_boxplot() +
  ggtitle("Speed of neutrophils migrating (vehicle)")
```
The distibutions differ significantly
```{r}
t.test( population %>% filter(Metadata_condition == "vehicle", Metadata_matrix == "FN") %>% extract2("Track_Speed"), 
        population %>% filter(Metadata_condition == "vehicle", Metadata_matrix == "HEM") %>% extract2("Track_Speed"))

```
```{r}
ggplot(data = population %>% filter(Metadata_matrix == "FN", Metadata_condition == "CP17") , aes(y = Track_xFMI, x = Metadata_dose)) +
    geom_boxplot()

ggplot(data = population %>% filter(Metadata_matrix == "FN", Metadata_condition == "SP17") , aes(y = Track_xFMI, x = Metadata_dose)) +
    geom_boxplot()

ggplot(data = population %>% filter(Metadata_matrix == "FN"), aes(y = Track_xFMI, x = Metadata_condition)) +
    geom_boxplot()

population %>%
  ungroup() %>%
  filter(Metadata_matrix == "HEM") %>%
  group_by(Metadata_matrix, Metadata_condition, Metadata_dose) %>% 
  summarise(mean_fmix = mean(Track_Speed)
  )
```
```{r}
ggplot(data=population %>% filter(Metadata_matrix == "FN"), aes(x=Track_xFMI, y = Track_Integrated_Distance_Traveled, color = Metadata_dose)) +
geom_point()

```


```{r}
ggplot(data = population %>% filter(Metadata_matrix == "FN"), aes(x=Track_xFMI)) + 
  geom_histogram()
```
```{r}
df <- population %>% 
  ungroup() %>% 
  filter( Metadata_condition %in% c("vehicle","control")) %>%
  group_by_(.dots = c("Metadata_id", "Metadata_condition")) %>%
  summarise_all("mean") %>%
  print
```
```{r}
df %>% ggplot(aes(x = Track_Speed, Track_xFMI, color = Metadata_condition)) +
  geom_point()
```

```{r}
population %>% 
  ungroup() %>%
  filter(Metadata_condition == "vehicle") %>%
  group_by(Metadata_id) %>%
  summarise(n = n())

population %>% 
  filter(Metadata_matrix == "FN", Metadata_id == "bd0054") %>%
  summarise(mean_xfmi = mean(Track_xFMI))
```


```{r}
feature_tsne = c("Track_Speed", "Track_Speed_Y", "Track_Speed_X", "Track_xFMI", "Track_yFMI",
                 "Track_Directionality", "Track_Distance_Traveled","Track_Integrated_Distance_Traveled", "Track_CI", "Track_Angle")

df <- normalized %>% 
  ungroup() %>%
  filter(Metadata_condition != "vehicle") %>%
  #filter(Metadata_condition != "control") %>%
  select_(.dots = c(feature_tsne,strata,"Track_Sector")) %>%
  group_by_(.dots = c("Metadata_matrix","Metadata_condition","Metadata_dose","Metadata_id")) %>%
  #group_by("Metadata_matrix) %>%
  #summarise(mean_speed = mean(Track_Speed)) %>% 
  summarise_all(c("mean","sd") %>%
  print
  

calculate_tsnes <- function(perplexity,data) {
  return(Rtsne(data, perplexity = perplexity, verbose = TRUE, max_iter = 500, theta = 0.5, pca_scale = TRUE))
}

perplexities <- c(16)

set.seed(42)
HEM <- df 
HEM_train <- HEM %>% ungroup() %>% select_(.dots = feature_tsne)
tsnes_hem <- lapply(perplexities, calculate_tsnes, data = HEM_train)

FN <- df %>% filter(Metadata_matrix == "FN")
FN_train <- FN %>% ungroup() %>% select_(.dots = feature_tsne)
tsnes_fn <- lapply(perplexities, calculate_tsnes, data = FN_train)

```



```{r}

 
for (i in 1){
  Y <- as.data.frame(tsnes_hem[[i]]$Y)

  df = cbind(as.data.frame(Y),
             as.data.frame(df))

  print(ggplot(data = df, aes(x = V1, y = V2, color = Metadata_matrix, size = 10, shape = factor(Metadata_dose))) +
      geom_point() +
      xlab("") + 
      ylab("") +
      ggtitle("t-SNE") +
      guides(colour = guide_legend(override.aes = list(size = 6))) +
      theme_light(base_size = 20) +
      theme(axis.text.x = element_blank(),
            axis.text.y = element_blank()) + 
      labs(title = sprintf('Migration in FN,  perplexity %f', tsnes_fn[[i]]$perplexity )))
}
```

```{r}
df_pca <- normalized %>% 
  ungroup() %>%
  select(feature_tsne)

pca <- prcomp(df_pca)

plot(pca)
```

```
