---
title: "Working title: CP17 migration data"
author: "TB"
date: "9/9/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
source("../windrose.r")
library("magrittr")
```



# Input data 
* The tracking data is stored in the file clean_tracks.csv.
* The normalized data is stored in the file clean_normalized.csv. Normalization can be found in 04_normalize.Rmd

```{r}
csv_tracks <- 'clean_tracks.csv'
csv_normalized <- 'clean_normalized.csv'
analysis_folder <- '../../../analysis/2017_04_28_matlab'
```

# Output folder
```{r}
image_folder <- file.path(analysis_folder, "image_data")
```

Definition of the grouping variables. 
```{r}
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')
```

Tracking and normalized data is loaded as a data frame, sorted and ordered 
```{r}
tracks <- read_csv(file.path(analysis_folder, csv_tracks)) %>%
  select(Metadata_id,Metadata_matrix, Metadata_condition, Metadata_dose, everything() ) %>%
  arrange(Metadata_id, Metadata_matrix, Metadata_condition, Metadata_dose) %>%
  group_by_(.dots = strata) 

normalized <- read_csv(file.path(analysis_folder, csv_normalized)) %>%
  select(Metadata_id,Metadata_matrix, Metadata_condition, Metadata_dose, everything() ) %>%
  arrange(Metadata_id, Metadata_matrix, Metadata_condition, Metadata_dose) %>%
  group_by_(.dots = strata)  %>%
  filter(Track_Length > 19)
```

Small trajectories are removed and the angles are scaled to [-pi, pi] and rotated 
(using neutrominer::track the angles were calculated with 0 degree set to three o 
clock, now we rotate zero 12 )

Small trajectories of neutrophils that are observred less than 20 frames are removed. 
```{r}
# angles are scaled to the intervale (-pi, pi)
population <- tracks %>%
  mutate(Track_Angle = Track_Angle + pi/2) %>% # rotate all angles by 90 degree or pi/2
  mutate(Track_Angle = ifelse(Track_Angle > pi, Track_Angle - 2*pi, Track_Angle) ) %>%
  mutate(Track_Angle = ifelse(Track_Angle < 0, Track_Angle + 2*pi, Track_Angle) ) 
```

## Quality 
To analyse the tracking quality we use cytominer::assess(). To compare the results of 
all migration run in FN and HEM we use the VOT (valid observation time). 

```{r}
quality <- tracks %>% 
  neutrominer::assess(min_path_length = 19)

quality %>% print


quality %>% 
  ungroup() %>%
  group_by(Metadata_matrix) %>% 
  summarise(mean_VOT = mean(VOT), sd_VOT = sd(VOT)) %>% 
  print()
```

Lets visually compare the results from both matrices
```{r}
ggplot(data = quality %>% filter(Metadata_matrix == 'FN'), 
       aes(x = VOT, y = Exp_Valid_Tracks, color = Metadata_id, shape = Metadata_condition)) +
  geom_point() +
  coord_cartesian(xlim = c(0, 1)) +
  ggtitle("Track Quality for migration in FN (high VOT is good)")
  
ggplot(data = quality %>% filter(Metadata_matrix == 'HEM'), 
       aes(x = VOT, y = Exp_Valid_Tracks, color = Metadata_id, shape = Metadata_condition)) +
  geom_point() +
  coord_cartesian(xlim = c(0, 1)) + 
  ggtitle("Track Quality for migration in HEM (high VOT is good)")

ggsave(file.path(image_folder, "track_quality_vot_hem.pdf"), plot = last_plot(), device = NULL, path = NULL,
  scale = 1, width = NA, height = NA, units = c("in", "cm", "mm"),
  dpi = 300, limitsize = TRUE)

```

Which patient ids belong to the migrations run in HEM?
```{r}
ids_cp17 <- tracks %>% 
  filter(Metadata_condition == "CP17", Metadata_matrix == "HEM") %>%
  ungroup() %>% 
  group_by(Metadata_id) %>% 
  slice(1) %>%
  extract2("Metadata_id") %>% 
  print

ids_sp17 <- tracks %>% 
  filter(Metadata_condition == "SP17", Metadata_matrix == "HEM") %>%
  ungroup() %>% 
  group_by(Metadata_id) %>% 
  slice(1) %>%
  extract2("Metadata_id") %>% 
  print

```

## Migration analysis

We look at the distribution of the direction and speed of the neutrophils run in HEM. 
Each condition (CP17, SP17, control and vehicle) is plotted separately.

## Remove clutter
We remove all short trajectories and transform the speed from µm/min to µm/sec.
```{r}
test_data <- population %>%
  filter(Metadata_matrix == "HEM", Track_Length > 19) %>% 
  mutate(Track_Speed = Track_Speed / 60)
```

Define parameters for the windrose plot
```{r}
spdmin <- 0
spdmax <- 0.3
spdres <- 0.02
dirres <- 90
```

Distribution of speed and angle for control and vehicle distribution.
```{r}
controls <- test_data %>% 
  filter(Metadata_condition == "control") 

vehicle <- test_data %>% 
  filter(Metadata_condition == "vehicle") 


h1 <- plot.windrose(spd = controls$Track_Speed, dir = (180 * (controls$Track_Angle) / pi),
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle and speed distribution for migration in HEM (control)")

ggsave(file.path(image_folder, "windrose_hem_control.pdf"), plot = last_plot(), device = NULL, path = NULL,
  scale = 1, width = NA, height = NA, units = c("in", "cm", "mm"),
  dpi = 300, limitsize = TRUE)

h2 <- plot.windrose(spd = vehicle$Track_Speed, dir = (180 * (vehicle$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres,  title_name = "Angle and speed distribution for migration in HEM (vehicle)")

ggsave(file.path(image_folder, "windrose_hem_vehicle.pdf"), plot = last_plot(), device = NULL, path = NULL,
  scale = 1, width = NA, height = NA, units = c("in", "cm", "mm"),
  dpi = 300, limitsize = TRUE)
```

Distribution of speed and angle for CP17 / SP17 and dose 0.5.
```{r}
CP17 <- test_data %>% 
  filter(Metadata_condition == "CP17") %>%
  filter(Metadata_dose == 0.5) 

SP17 <- test_data %>% 
  filter(Metadata_condition == "SP17") %>%
  filter(Metadata_dose == 0.5) 


h <- plot.windrose(spd = CP17$Track_Speed, dir = (180 * (CP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle and speed distribution for migration in HEM with  CP17, dose 0.5)")

ggsave(file.path(image_folder, "windrose_hem_CP17_0.5.pdf"), plot = last_plot(), device = NULL, path = NULL,
  scale = 1, width = NA, height = NA, units = c("in", "cm", "mm"),
  dpi = 300, limitsize = TRUE)


h <- plot.windrose(spd = SP17$Track_Speed, dir = (180 * (SP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle and speed distribution for migration in HEM with  SP17, dose 0.5)")

ggsave(file.path(image_folder, "windrose_hem_SP17_0.5.pdf"), plot = last_plot(), device = NULL, path = NULL,
  scale = 1, width = NA, height = NA, units = c("in", "cm", "mm"),
  dpi = 300, limitsize = TRUE)

```
```{r}
CP17 <- test_data %>% 
  filter(Metadata_condition == "CP17") %>%
  filter(Metadata_dose == 5) 

SP17 <- test_data %>% 
  filter(Metadata_condition == "SP17") %>%
  filter(Metadata_dose == 5) 


h <- plot.windrose(spd = CP17$Track_Speed, dir = (180 * (CP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle and speed distribution for migration in HEM with  CP17, dose 5)")

ggsave(file.path(image_folder, "windrose_hem_CP17_5.pdf"), plot = last_plot(), device = NULL, path = NULL,
  scale = 1, width = NA, height = NA, units = c("in", "cm", "mm"),
  dpi = 300, limitsize = TRUE)


h <- plot.windrose(spd = SP17$Track_Speed, dir = (180 * (SP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle and speed distribution for migration in HEM with  SP17, dose 5)")

ggsave(file.path(image_folder, "windrose_hem_SP17_5.pdf"), plot = last_plot(), device = NULL, path = NULL,
  scale = 1, width = NA, height = NA, units = c("in", "cm", "mm"),
  dpi = 300, limitsize = TRUE)

```

```{r}
CP17 <- test_data %>% 
  filter(Metadata_condition == "CP17") %>%
  filter(Metadata_dose == 50) 

SP17 <- test_data %>% 
  filter(Metadata_condition == "SP17") %>%
  filter(Metadata_dose == 50) 


h <- plot.windrose(spd = CP17$Track_Speed, dir = (180 * (CP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle and speed distribution for migration in HEM with  CP17, dose 50)")

ggsave(file.path(image_folder, "windrose_hem_CP17_50.pdf"), plot = last_plot(), device = NULL, path = NULL,
  scale = 1, width = NA, height = NA, units = c("in", "cm", "mm"),
  dpi = 300, limitsize = TRUE)


h <- plot.windrose(spd = SP17$Track_Speed, dir = (180 * (SP17$Track_Angle) / pi), 
  spdmin = spdmin, spdmax = spdmax, spdres = spdres, dirres = dirres, title_name = "Angle and speed distribution for migration in HEM with  SP17, dose 50)")

ggsave(file.path(image_folder, "windrose_hem_SP17_50.pdf"), plot = last_plot(), device = NULL, path = NULL,
  scale = 1, width = NA, height = NA, units = c("in", "cm", "mm"),
  dpi = 300, limitsize = TRUE)

```


We calculate the fration of tracks migrating in each direction.
```{r}
sector_fraction <- normalized %>% 
  filter(Metadata_matrix == "HEM") %>%
  group_by_(.dots = strata) %>%
  summarise(positive = sum(Track_Positive_Sector) / n(),
            negative = sum(Track_Negative_Sector) / n(),
            neutral_up = sum(Track_Neutral_Sector_Up) / n(),
            neutral_down = sum(Track_Neutral_Sector_Down) / n()
    )

sector_fraction_condition <- sector_fraction %>%
  ungroup() %>%
  group_by(Metadata_matrix) %>%
  summarise(mean_positive = mean(positive),
            sd_positive = sd(positive),
            mean_negative = mean(negative),
            sd_negative = sd(negative),
            mean_neutral_up = mean(neutral_up),
            sd_neutral_up = sd(neutral_up),
            mean_neutral_down = mean(neutral_down),
            sd_neutral_down = sd(neutral_down)
            ) %>%
  print
```

Do we see a difference in the conditions? 
 

```{r}
sector_fraction_condition <- sector_fraction %>%
  ungroup() %>%
  group_by(Metadata_matrix, Metadata_condition, Metadata_dose) %>%
  summarise(mean_positive = mean(positive),
            sd_positive = sd(positive),
            mean_negative = mean(negative),
            sd_negative = sd(negative),
            mean_neutral_up = mean(neutral_up),
            sd_neutral_up = sd(neutral_up),
            mean_neutral_down = mean(neutral_down),
            sd_neutral_down = sd(neutral_down)
            ) %>%
  print

```
## Comparison of all sectors. 


```{r}
ttest_speed_with_dose <- function(dose){
cp <- normalized %>%
  filter(Metadata_condition == "CP17", Metadata_matrix == "HEM", Metadata_dose == dose) 
sp <- normalized %>%
  filter(Metadata_condition == "SP17", Metadata_matrix == "HEM", Metadata_dose == dose)
return(t.test(cp$Track_Speed, sp$Track_Speed))
}

speed_dose_p_values <- lapply(c(0.5,5,50), ttest_speed_with_dose) %>% print

```

```{r}

ttest_dose_sector <- function(dose, sector, feature){
cp <- normalized %>%
  filter(Metadata_condition == "CP17") %>%
  filter(Metadata_matrix == "HEM") %>% 
  filter(Metadata_dose == dose) %>%
  filter(Track_Sector == sector) %>% 
  extract2(feature)

sp <-  normalized %>%
  filter(Metadata_condition == "SP17") %>%
  filter(Metadata_matrix == "HEM") %>% 
  filter(Metadata_dose == dose) %>%
  filter(Track_Sector == sector) %>% 
  extract2(feature)

t <- t.test(cp, sp)
return(t$p.value)
}



p_values <- rbind(
c("Track_Speed",1,sapply(c(0.5, 5, 50), ttest_dose_sector, sector = 1, feature = "Track_Speed")),
c("Track_Speed",2,sapply(c(0.5, 5, 50), ttest_dose_sector, sector = 2, feature = "Track_Speed")),
c("Track_Directionality",1,sapply(c(0.5, 5, 50), ttest_dose_sector, sector = 1, feature = "Track_Directionality")), 
c("Track_Directionality",2,sapply(c(0.5, 5, 50), ttest_dose_sector, sector = 2, feature = "Track_Directionality")),
c("Track_xFMI",1,sapply(c(0.5, 5, 50), ttest_dose_sector, sector = 1, feature = "Track_xFMI")),
c("Track_xFMI",2,sapply(c(0.5, 5, 50), ttest_dose_sector, sector = 2, feature = "Track_xFMI")),
c("Track_yFMI",1,sapply(c(0.5, 5, 50), ttest_dose_sector, sector = 1, feature = "Track_yFMI")),
c("Track_yFMI",2,sapply(c(0.5, 5, 50), ttest_dose_sector, sector = 2, feature = "Track_yFMI")),
c("Track_CI",1,sapply(c(0.5, 5, 50), ttest_dose_sector, sector = 1, feature = "Track_CI")),
c("Track_CI",2,sapply(c(0.5, 5, 50), ttest_dose_sector, sector = 2, feature = "Track_CI"))
  
)

colnames(p_values) <- c("feature","sector","dose 0.5","dose 5", "dose 50")

p_values %>% print

```

```{r}

ttest_dose_sector_complete <- function(dose, sector, feature){
cp <- population %>%
  filter(Metadata_condition == "CP17") %>%
  filter(Metadata_matrix == "HEM") %>% 
  filter(Metadata_dose == dose) %>%
  filter(Track_Sector == sector) %>% 
  extract2(feature)

sp <-  population %>%
  filter(Metadata_condition == "SP17") %>%
  filter(Metadata_matrix == "HEM") %>% 
  filter(Metadata_dose == dose) %>%
  filter(Track_Sector == sector) %>% 
  extract2(feature)

t <- t.test(cp, sp)
return(t)
}

ttest_dose_sector_complete(5, 2, "Track_yFMI")
```
```{r}
population %>% 
  filter(Metadata_matrix == "HEM") %>%
  filter(Metadata_dose == 5) %>%
  group_by_(.dots = strata) %>%
  select(Track_xFMI, Track_yFMI, Track_Distance_Traveled) %>%
  summarise_all(.funs = mean)
```

```{r}
ggplot(data = tracks %>% filter(Track_Length > 19), aes(x = Track_xPos, y = Track_xFMI)) + geom_point()

ggplot(data = tracks %>% filter(Track_Length > 19), aes(x = Track_xPos, y = Track_Speed)) + geom_point()

```
```{r}
lin_model <- lm(formula = Track_xPos ~ Track_Directionality, data = tracks %>% filter(Track_Length > 19)) 
summary(lin_model)
```

We collapse all values to experiments 
```{r}
collapsed <- normalized %>% 
  filter(Track_Length > 19) %>%
  ungroup %>% 
  select(-Metadata_id ) %>%
  group_by(Metadata_matrix, Metadata_condition, Metadata_dose ) %>%
  summarise_all(.funs = mean) %>% 
  print


ggplot(data = collapsed %>%  
    filter(Metadata_matrix == "FN") %>%
    filter(Metadata_condition %in% c("CP17","SP17","control"))) + 
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

ggplot(data = collapsed %>%  
    filter(Metadata_matrix == "HEM") %>%
    filter(Metadata_condition %in% c("CP17","SP17","control"))) + 
  aes(x = Track_Speed, y = Track_xFMI, shape = factor(Metadata_condition), color = Metadata_dose )  +
  geom_point()

```
