---
title: "load_data"
author: "TB"
date: "07/07/2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("magrittr")
source("../multiplot.r")
```
# How does different normalization schemes affect our tracking data 
This notebooks compares the effect of different peptides to the chemotaxis of neutrophiles.

Our data set consists of cell tracking data run with different conditions.

Each time series characterizes the chemotaxis of neutrophils in an in vitro assay. In the analysed experiments the chemoattractant interleukin 8 was used to create an gradient that directs from the left border of the images / channel to the left channel.
For each patient or experiment id ("Metadata_id") a set of five (FN) or six (HEM) time series were recorded consisting of 
* one control run, "Metadata_condition" = "control"
* one vehicle run, "Metadata_condition" = "vehicle"
* three runs with "Metadata_condition" "CP17" or "SP17" in with different doses Metadata_dose = c(0.5, 5, 50)

The experiments for each patient are either run in the matrix HEM or FN specified as "Metadata_matrix" = "FN" or "HEM". For all patients that have been run in HEM, one additional run with "Metadata_condition" = "vehicle" was run using the matrix "FN". 


# Load data 
Load tracking data created using MATLAB. 
```{r}
csv_tracks <- 'clean_tracks.csv'
csv_normalized <- 'clean_normalized.csv'
analysis_folder <- '../../../analysis/2017_04_28_matlab/'

df <- read_csv(file.path(analysis_folder, csv_tracks)) %>%
  filter(Track_Length > 19) 
```
Experiments are groupes by condition, dose, id, data and matrix
```{r}
# grouping variables 
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')
```

List all IDs and the matrix used in this experiment (either HEM or FN).
```{r}
df_id_matrix <- df %>%
  filter(Metadata_condition == "control") %>%
  select(Metadata_id, Metadata_matrix) %>%
  group_by(Metadata_id) %>%
  slice(1) %>%
  print
```
We define the variables for normalization 
```{r}
feature_var = c(
  "Track_Speed",
  "Track_Speed_Y",
  "Track_Speed_X",
  "Track_xFMI",
  "Track_yFMI",
  "Track_Directionality",
  "Track_Distance_Traveled","Track_CI"
  )
```

Remove data set bd0055 (technical error, very few cells at the "gate" of the channel).
```{r}
population <- df %>%
  filter(Metadata_id != "bd0055") %>% 
  filter(Metadata_id != "gn0017")
```

# Normalize against vehicle group
All experiments run in HEM. For each ID (Metadata_id) six experiments were run either using SP17 or CP17
1. SP17 / CP17 with dose 0.5
2. SP17 / CP17 with dose 5
3. SP17 / CP17 with dose 50
4. Control
5. Vehicle
6. Vehicle using matrix FN

## Define control population
To normalize against Vehicle, all vehicle runs in FN are removed from the 
sample group used for normalization. First, we list all IDs run in HEM.
```{r}
# define control group
id_hem <- df_id_matrix %>%
  filter(Metadata_matrix == "HEM") %>%
  extract2("Metadata_id") %>% 
  print 
```

```sample``` defines the population used for normalization. For all IDs run
in HEM, the vehicle migratons run in FN are removed.
```{r}
sample <- population %>% 
  filter(Metadata_condition == "vehicle") %>%
  filter( !((Metadata_id %in% id_hem) & (Metadata_matrix == "FN") ))
```

## Create normalized profiles.
```{r}
normalized <-
  cytominer::normalize(
    population = population %>% 
       filter( !((Metadata_id %in% id_hem) & (Metadata_matrix == "FN") )),
    variables = feature_var,
    strata =  "Metadata_id",
    sample = sample,
    operation = "standardize"
  ) 
```

Optional: Profiles are collapsed to sectors
```{r}
sectors <- 
  cytominer::aggregate(
    population = normalized,
    variables = feature_var,
    strata  = c("Metadata_matrix","Metadata_id", "Metadata_condition", "Metadata_dose","Track_Sector"),
    operation = "mean" 
  )
```

# Results

## Differences SP17 vs CP17

ttest_dose is a wrapper function for a ttest.
```{r}
ttest_dose <- function(dose = 5, feature = "Track_Speed", matrix = "FN"){
cp <- normalized %>%
  filter(Metadata_condition == "CP17") %>%
  filter(Metadata_matrix == matrix) %>% 
  filter(Metadata_dose == dose) %>%
  extract2(feature)

sp <-  normalized %>%
  filter(Metadata_condition == "SP17") %>%
  filter(Metadata_matrix == matrix) %>% 
  filter(Metadata_dose == dose) %>%
  extract2(feature)

t <- t.test(cp, sp)
return(t)
}
```

## CP17 vs SP17 
Analysis of migration run FN with inhibitor CP17 vs. control experiment run with SP17.

### Summary Track_Speed
* Migration in CP17 is 44% slower compared to the vehicle experiments 
* Migration in SP17 is 17% faster compared to vehicle 
* CP17 and SP17 differ significantly with  p-value = 8.563e-06

```{r}
ttest_dose(feature = "Track_Speed")
```

### Summary Track_Directionality
* Migration in CP17 shows an decrease of 29% compared to control
* Migration in SP17 shows an increase of 4% compared to control
* CP17 has an significantly decreased directionality with p-value = 0.01268

```{r}
ttest_dose(feature = "Track_Directionality")
```
### Summary Track_xFMI
* Migration in CP17 is decreased by 22%. As the xFMI is negative, the xFMI becomes even more directed! 
* Migration in SP17 increased by 29%.
* CP17 shows a significantly decreased xFMI compared to SP17 with 3.96e-06.
```{r}
#  
population %>% 
  filter(Metadata_dose == 5, Metadata_matrix == "FN") %>%
  summarise(xFMI = mean(Track_xFMI))

ttest_dose(feature = "Track_xFMI")

```
```{r}
normalized %>% 
   filter(Metadata_dose != 0.5, Metadata_condition != "control", Metadata_matrix == "FN")  %>%
  group_by(Metadata_condition, Metadata_dose, Metadata_matrix) %>% 
  summarise(mean_speed = mean(Track_Speed), median_speed = median(Track_Speed), n = n())
```

```{r}
df <- 
  normalized %>% 
  filter(Metadata_dose != 0.5, Metadata_condition != "control", Metadata_matrix == "FN") 

ggplot(data = df) +
  aes(y = Track_Speed, fill = Metadata_condition, x = Metadata_dose) + 
  geom_boxplot(notch = TRUE) 

ggplot(data = df) +
  aes(y = Track_Directionality, fill = Metadata_condition, x = Metadata_dose) + 
  geom_boxplot(notch = TRUE) 

ggplot(data = df) +
  aes(y = Track_xFMI, fill = Metadata_condition, x = Metadata_dose) + 
  geom_boxplot(notch = TRUE) 

```

```{r}
ttest_dose_sector_complete <- function(dose = 5, sector = 1, feature = "Track_Speed", matrix = "FN"){
cp <- normalized %>%
  filter(Metadata_condition == "CP17") %>%
  filter(Metadata_matrix == matrix) %>% 
  filter(Metadata_dose == dose) %>%
  filter(Track_Sector == sector) %>% 
  extract2(feature)

sp <-  normalized %>%
   filter(Metadata_id != "bd0055") %>%
  filter(Metadata_condition == "SP17") %>%
  filter(Metadata_matrix == matrix) %>% 
  filter(Metadata_dose == dose) %>%
  filter(Track_Sector == sector) %>% 
  extract2(feature)

t <- t.test(cp, sp)
return(t)
}
```
## Sectoranalysis
```{r}
ttest_dose_sector_complete(sector = 1, feature = "Track_Speed")
ttest_dose_sector_complete(sector = 1, feature = "Track_Directionality")
ttest_dose_sector_complete(sector = 1, feature = "Track_xFMI")
```


```{r}
ttest_dose_sector_complete(sector = 2, feature = "Track_Speed")
ttest_dose_sector_complete(sector = 2, feature = "Track_Directionality")
ttest_dose_sector_complete(sector = 2, feature = "Track_xFMI")
```
We observe no difference in the number of trakcs in each sector. 
```{r}
sector_fraction <- normalized %>% 
  filter(Metadata_matrix == "FN", Metadata_dose %in% c(50)) %>%
  group_by_(.dots = strata) %>%
  summarise(positive = sum(Track_Positive_Sector) / n(),
            negative = sum(Track_Negative_Sector) / n(),
            neutral_up = sum(Track_Neutral_Sector_Up) / n(),
            neutral_down = sum(Track_Neutral_Sector_Down) / n()
    ) %>% 
  print

t.test(
  sector_fraction %>%
  filter(Metadata_condition == "CP17") %>%
  extract2("positive"),
  sector_fraction %>%
  filter(Metadata_condition == "SP17") %>%
  extract2("positive")
)

t.test(
  sector_fraction %>%
  filter(Metadata_condition == "CP17") %>%
  extract2("negative"),
  sector_fraction %>%
  filter(Metadata_condition == "SP17") %>%
  extract2("negative")
)
```
## Sneaker, walker, runner 
Now we define slow, normal and fast cells as sneaker, walker and runner. 
```{r}
quantiles <- normalized %>% 
  filter(Metadata_condition == "vehicle") %>%
  filter(Metadata_matrix == "FN") %>%
  extract2("Track_Speed") %>%
  quantile(.,probs = c(.25, .75)) %>% 
  as.vector()
```

Summary:
* Sneaker
  * more snekaer in CP17 with dose = 5    0.0767
                          and dose = 50   0.0057
* Walker
  * more walker in CP17 with dose = 5     0.1708
  * more walker in SP17 with dose = 50    0.0551
* Runner
  * more runner in SP17 with dose = 5     0.0004
                         and dose = 50    0.6376
```{r}
movements <- normalized %>% 
  filter(Metadata_matrix == "FN", Metadata_dose != 0.5) %>%
  mutate(sneaker = (Track_Speed < quantiles[[1]])) %>%
  mutate(walker = ( (Track_Speed > quantiles[[1]] )  & ( Track_Speed < quantiles[[2]] ) ) )  %>%
  mutate(runner = (Track_Speed > quantiles[[2]])) %>%
  print

movements %>%  
  ungroup() %>% 
  group_by(Metadata_dose, Metadata_condition) %>%
  summarise(mean_sneaker = mean(sneaker), #sd_sneaker = sd(sneaker),
            mean_walker = mean(walker), #sd_walker = sd(walker),
            mean_runner = mean(runner), #sd_runner = sd(runner), 
            n = n()
    )
```
Which of these differences is significant?
```{r}
t.test(
  movements %>% filter(Metadata_dose == 5, Metadata_condition == "SP17") %>% extract2("sneaker"), 
  movements %>% filter(Metadata_dose == 5, Metadata_condition == "CP17") %>% extract2("sneaker")
)$p.value

t.test(
  movements %>% filter(Metadata_dose == 50, Metadata_condition == "SP17") %>% extract2("sneaker"), 
  movements %>% filter(Metadata_dose == 50, Metadata_condition == "CP17") %>% extract2("sneaker")
)$p.value

t.test(
  movements %>% filter(Metadata_dose == 5, Metadata_condition == "SP17") %>% extract2("walker"), 
  movements %>% filter(Metadata_dose == 5, Metadata_condition == "CP17") %>% extract2("walker")
)$p.value

t.test(
  movements %>% filter(Metadata_dose == 50, Metadata_condition == "SP17") %>% extract2("walker"), 
  movements %>% filter(Metadata_dose == 50, Metadata_condition == "CP17") %>% extract2("walker")
)$p.value

t.test(
  movements %>% filter(Metadata_dose == 5, Metadata_condition == "SP17") %>% extract2("runner"), 
  movements %>% filter(Metadata_dose == 5, Metadata_condition == "CP17") %>% extract2("runner")
)$p.value

t.test(
  movements %>% filter(Metadata_dose == 50, Metadata_condition == "SP17") %>% extract2("runner"), 
  movements %>% filter(Metadata_dose == 50, Metadata_condition == "CP17") %>% extract2("runner")
)$p.value
```

```{r}
population %>% 
  group_by(Metadata_id, Metadata_condition) %>% 
  filter(Metadata_matrix == "FN") %>% 
  summarise(mean_xfmi = mean(Track_xFMI)) 
```
```{r}
normalized %>% 
  filter(Metadata_condition == "CP17") %>% 
    ggplot(data = .) +
  aes(x = Metadata_dose, y = Track_Speed, fill = Metadata_matrix) +
  geom_boxplot()

normalized %>% 
  filter(Metadata_condition == "CP17") %>% 
    ggplot(data = .) +
  aes(x = Metadata_dose, y = Track_Directionality, fill = Metadata_matrix) +
  geom_boxplot()

normalized %>% 
  filter(Metadata_condition == "CP17") %>% 
    ggplot(data = .) +
  aes(x = Metadata_dose, y = Track_xFMI, fill = Metadata_matrix) +
  geom_boxplot()

```
