---
title: "load_data"
author: "TB"
date: "5/15/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library("tibble")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("purrr")
library("broom")
library("dplyr")
library("tsne")
library("ggfortify")
library("cluster")
library('magrittr')
# load cytominer 

```

In this notebook we compare the migration results of the CP tracking with the matlab tracking results. 
The matlab tracking is used as a standard and not changed.  

Only three videos are used for this comparison
Metadata_id gn0017 with
*  Metadata_condition == control, and 
* Metadata_condition == CP17 & dose 0.5 and 
* Metadata_condition == CP17 & dose 5 

These are randomly chosen. We limit ourselves to three so we are able to fastly iterate through different parameter settings for CP. 


# Load tracking data tracking data 

```{r}
# define grouping variables 
strata <- c('Metadata_id','Metadata_condition','Metadata_dose','Metadata_date','Metadata_matrix')

# load matlab data 
population_matlab <- read_csv('../../../analysis/2017_04_28_matlab/clean_tracks.csv') %>%
  group_by_(.dots = strata)

population_matlab %<>% 
  filter( (Metadata_id == 'gn0017')) %>%
  filter( Metadata_condition == 'control' | ( Metadata_condition == 'CP17' & (Metadata_dose == 0.5 | Metadata_dose == 5))) %>%
  group_by_(.dots = strata)

population_cp_lap <- read.csv('../../../analysis/2017_06_morph_gradient_lap/TrackeddetectedNeutros.csv') %>%
   rename(Metadata_timePoint = Metadata_frame) %>%
   group_by_(.dots =  c(strata,'TrackObjects_Label')) %>%
   arrange(Metadata_timePoint) %>%
   cytominer::track(., c(strata,'TrackObjects_Label')) %>%
   group_by_(.dots = strata) 

population_cp_lap_1p <- read.csv('../../../analysis/2017_07_morph_gradient_lap_1phase/TrackeddetectedNeutros.csv') %>%
   rename(Metadata_timePoint = Metadata_frame) %>%
   group_by_(.dots =  c(strata,'TrackObjects_Label')) %>%
   arrange(Metadata_timePoint) %>%
   cytominer::track(., c(strata,'TrackObjects_Label')) %>%
   group_by_(.dots = strata)   

population_cp <- read.csv('../../../analysis/2017_06_morph_gradient/TrackeddetectedNeutros.csv') %>%
   rename(Metadata_timePoint = Metadata_frame) %>%
   group_by_(.dots =  c(strata,'TrackObjects_Label_30')) %>%
   arrange(Metadata_timePoint) %>%
   cytominer::track(., c(strata,'TrackObjects_Label_30')) %>%
   group_by_(.dots = strata) 



```

assess the tracking quality using cytominer::assess
```{r}
quality_list <-  list(cytominer::assess(population_matlab, 20, strata),
  cytominer::assess(population_cp, 20, strata),
  cytominer::assess(population_cp_lap, 20, strata),
  cytominer::assess(population_cp_lap_1p, 20, strata))

quality_list[[1]] %<>% 
  mutate(algorithm = 'MATLAB') %>% 
  mutate(Metadata_id = tolower(Metadata_id))

quality_list[[2]] %<>% 
  mutate(algorithm = 'CP') %>% 
  mutate(Metadata_id = tolower(Metadata_id))

quality_list[[3]] %<>% 
  mutate(algorithm = 'CP LAP') %>% 
  mutate(Metadata_id = tolower(Metadata_id))

quality_list[[4]] %<>% 
  mutate(algorithm = 'CP LAP 1P') %>% 
  mutate(Metadata_id = tolower(Metadata_id))

quality2 <- do.call(rbind, quality_list)

```


# All experiments are ordered by theri VOT
```{r}
ggplot(data = quality2, aes(x = VOT, y = Exp_Valid_Tracks, color = algorithm, shape = Metadata_dose)) +
  geom_point() 
  # coord_fixed() 
  #xlim(0,1) +
  #ylim(0,1)
```

```{r}
ggplot(data = quality2, aes(x = Exp_Mean_Track_Life_Time, y = Exp_Valid_Tracks, color = algorithm, shape = Metadata_dose)) +
  geom_point() 


```

```{r}
quality2 %>% 
  ungroup() %>%
  group_by_('algorithm') %>%
  summarise(vot = mean(VOT),
            track_length = mean(Exp_Mean_Track_Life_Time)) %>%
  print

quality2 %>% 
  ungroup() %>%
  group_by(Metadata_condition, Metadata_dose) %>%
  summarise(vot = mean(VOT),
            track_length = mean(Exp_Mean_Track_Life_Time)) %>%
  print

```
```{r}
quality2 %>% 
  ungroup() %>%
  group_by(algorithm,Metadata_condition, Metadata_dose) %>%
  summarise(mean_vot = mean(VOT)) %>% 
  arrange(mean_vot) %>%
  print
```