---
title: "load_data"
author: "TB"
date: "5/15/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library("tibble")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("purrr")
library("broom")
library("dplyr")
library("tsne")
library("ggfortify")
library("cluster")
library("magrittr")
library("knitr")
library("corrplot")
#library("cytominer")
# load cytominer 

```

# Load data 
The output of CellProfiler track module is loaded as CSV, tracked using cytominer::track and 
stored in the data folder as "track.csv". Once the data is stored, the processing is not repeated;
instead "tracks.csv" is loaded. 
```{r}
csv_in <- 'TrackeddetectedNeutros.csv'
csv_out <- 'tracks.csv'
data_dir <- '../../../analysis/2017_morph_gradient_2/'
strata <- c('Metadata_condition','Metadata_dose','Metadata_id','Metadata_date','Metadata_matrix')

df <- data.frame()

for (iDir in list.dirs(data_dir)) {
  file_name <-  file.path(iDir, csv_in)
  print(file_name)
  if (file.exists(file_name)) {
    df <- rbind(df,suppressMessages(read_csv(file_name)))
  }
}


df %<>% dplyr::mutate(Metadata_frame = as.double(Metadata_frame)) 

#The data contains tracking data for neutrophils from different conditions. The datasets 
#can be ditinguished using the Metadata columns defined in strata. 
track_label = c('TrackObjects_Label_30')

tracks <- df %>% 
  rename(Metadata_timePoint = Metadata_frame) %>%
  group_by_(.dots =  c(strata,track_label)) %>%
  arrange(Metadata_timePoint) %>%
  cytominer::track(., c(strata,track_label)) %>%
  group_by_(.dots = strata) 
  
write_csv(tracks, file.path(data_dir, csv_out))
```

The quality of the tracking can be assessed using the cytominer::assess function. 
The VOT (valid observation time) column can be used to get a rough estimate of the 
track quality. 
```{r}
tracks %<>% group_by_(.dots = strata)

quality <- cytominer::assess(tracks, 19, strata)

quality %<>% full_join(., 
  tracks %>% 
    filter(Track_Length > 19) %>%
    summarise(mean_xFMI = mean(Track_xFMI)), 
  by = strata)
  
quality[is.na(quality)] <- 0
quality %>% knitr::kable()
```
Select the experiments with a VOT smaller 0.6. Most of these data sets belong to one ID ("GN0033", ie one human donor)
```{r}
quality %>% 
  filter(VOT < 0.7 ) %>% 
  knitr::kable()

quality %>% 
  filter(Metadata_id == "GN0033") %>% 
  knitr::kable()
```

To assess the tracking quality in one view it is usefull to plot the distribution of the VOT and the fraction valid tracks. 
```{r}
ggplot(quality, aes(VOT)) +
  geom_histogram(binwidth = 0.025)

ggplot(quality, aes(Exp_Valid_Track_Fraction)) +
  geom_histogram(binwidth = 0.04)

ggplot(quality,aes(x = VOT,y = Exp_Tracks))  +
  geom_point(aes(colour = Metadata_condition, shape = Metadata_matrix))

ggplot(quality,aes(x = Exp_Tracks,y = mean_xFMI))  +
  geom_point(aes(colour = Metadata_condition, shape = Metadata_matrix))
```

```{r}
valid_tracks <- tracks %>%
  filter(Track_Life_Time > 19)

ggplot(data = valid_tracks, aes(Track_Angle)) +
   geom_histogram(binwidth = 0.04)

x <- hist(valid_tracks$Track_Angle, plot = FALSE)

```


```{r}

tracks_valid <- tracks %>% filter(Track_Length > 19)

summary_speed <- tracks_valid %>% 
  ungroup() %>%
  group_by(Metadata_matrix, Metadata_condition, Metadata_dose) %>%
  summarise(mean_speed = mean(Track_Speed),std_speed = sd(Track_Speed))
  
summary_speed %>% knitr::kable()

ggplot(data = tracks_valid, aes(x = Track_Speed)) +
  geom_histogram(binwidth = 1)

```
# Normalize data
Data normalization is performed using cytominer::normalize. Normalization is performed using the "control" group; these 
migrations have been run without chemotaxis (no IL-8, i.e. no chemoattractant)

```{r}
population <- tracks %>% 
  filter(Track_Length > 19) %>% 
  na.omit() %>%
  ungroup(.)

# define values that can be normalized 
variables <- c("Track_Speed", "Track_Directionality","Track_xFMI","Track_yFMI","Track_Distance_Traveled","Track_Speed_Y","Track_Speed_X")

population <- cytominer::generalized_log(population, variables = variables)

normalized <-
  cytominer::normalize(
    population = population,
    variables = variables,
    strata =  'Metadata_id',
    sample = population %>% filter(Metadata_condition == 'vehicle'),
    operation = 'robustize'
  )

normalized %<>% dplyr::collect() 

ggplot(data = population, aes(x = Metadata_id, y = Track_xFMI)) +
  geom_boxplot() 

ggplot(data = normalized %>% filter(Metadata_condition == "control"), aes(x = Metadata_id, y = Track_xFMI)) +
  geom_boxplot() 

ggplot(data = normalized %>% filter(Metadata_condition == "vehicle"), aes(x = Metadata_id, y = Track_xFMI)) +
  geom_boxplot() 

```
# Normalized vs. not normalized data
We analyze the effect of the normalization by visalizing different properties of the 
migration experiments run using Fibronektin
```{r}
test_data <-  population %>% 
  filter(Metadata_matrix == "FN") %>%
  filter(Metadata_condition != "water")

test_data_normalized <- normalized %>% 
  filter(Metadata_matrix == "FN") %>%
  filter(Metadata_condition != "water")

ggplot(data = test_data, aes(x = Metadata_condition, y = Track_xFMI)) +
  geom_boxplot() +
  ggtitle("Migration in FN, track length >=20")

ggplot(data = test_data_normalized, aes(x = Metadata_condition, y = Track_xFMI)) +
  geom_boxplot() +
  ggtitle("Migration in FN, track length >=20, normalized")
```

# Directionality
```{r}
ggplot(data = test_data, aes(x = Track_Directionality,fill = Metadata_condition)) + 
  geom_histogram(binwidth = 0.05) +
  ggtitle("Migration in FN, track length >=20")

ggplot(data = test_data_normalized, aes(x = Track_Directionality,fill = Metadata_condition)) + 
  geom_histogram(binwidth = 0.05) +
  ggtitle("Migration in FN, track length >=20, normalized")

```



# x forward migration index 
```{r}
ggplot(data = test_data, aes(x = Track_xFMI,fill = Metadata_condition)) + 
  geom_histogram(binwidth = 0.02) +
  ggtitle("Migration in FN, track length >=20")

ggplot(data = test_data, aes(x = Track_xFMI,colour = Metadata_condition)) + 
  geom_freqpoly(binwidth = 0.02) +
  ggtitle("Migration in FN, track length >=20")

ggplot(data = test_data_normalized, aes(x = Track_xFMI,fill = Metadata_condition)) + 
  geom_histogram(binwidth = 0.1) +
  ggtitle("Migration in FN, track length >=20, normalized")

ggplot(data = test_data_normalized, aes(x = Track_xFMI,colour = Metadata_condition)) + 
  geom_freqpoly(binwidth = 0.1) +
  ggtitle("Migration in FN, track length >=20, normalized")

```

```{r}

ggplot(data = test_data %>% filter(Metadata_condition != 'vehicle'), aes(x = Track_xFMI, y = Track_CI)) +
  geom_point(aes(colour = Metadata_condition)) +
  ggtitle("Migration in FN, track length >=20")
  
ggplot(data = test_data_normalized %>% filter(Metadata_condition != 'vehicle'), aes(x = Track_xFMI, y = Track_CI)) +
  geom_point(aes(colour = Metadata_condition))  +
  ggtitle("Migration in FN, track length >=20, normalized")
```


```{r}
ggplot(data = test_data_normalized %>% filter(Metadata_condition == 'CP17'), aes(x = factor(Track_Sector), y = Track_xFMI)) +
  geom_boxplot() +
  ggtitle("Migration in FN, track length >=20, normalized")

ggplot(data = test_data_normalized %>% filter(Metadata_condition == 'control'), aes(x = factor(Track_Sector), y = Track_xFMI)) +
  geom_boxplot( ) +
  ggtitle("Migration in FN, track length >=20, normalized")
```
```{r}
ggplot(data = test_data_normalized %>% filter(Metadata_condition == 'control'), aes(x = Metadata_id, y = Track_xFMI)) +
  geom_boxplot( outlier.shape = NA) +
  ggtitle("Migration in FN, track length >=20, normalized")

ggplot(data = test_data_normalized %>% filter(Metadata_condition == 'CP17'), aes(x = Metadata_id, y = Track_xFMI)) +
  geom_boxplot( outlier.shape = NA) +
  ggtitle("Migration in FN, track length >=20, normalized")
```
# cluster the data 
```{r}
data <- normalized %>% 
  select(one_of(c(variables)))
corrplot(cor(data))
```